### 2025-02-16 src/appendices/appendix1.qmd
Initialize repository

# Appendix A

## EC Interpretations

1. Academic warning is treated the same way as Academic Probation when a brother has not had classes for a semester.
1. Standards Board does NOT need to automatically recommend a brother for suspension if said brother is brought up for standards with the possibility of suspension.
1. When adding interpretations, make sure to reference the particular bylaw being interpreted and the year the interpretation was made.

### 2025-02-16 src/appendices/appendix2.qmd
Initialize repository

# Appendix B

## Standards Rulings

1. September 25, 2010

   Charges: A brother was under a 2.2 GPA for two consecutive semesters.

   Plea: Responsible.

   Sanctions: Recommendation for suspension, voting privileges suspended until off of academic probation.

1. September 25, 2010

   Charges: A brother was under a 2.2 GPA for two consecutive semesters. Brother was currently on co-op.

   Plea: No Contest.

   Sanctions: Recommendation for suspension, voting privileges revoked upon return from co-op.

1. October 22, 2010

   Charges: A brother was living outside of the house without permission from the chapter. Plea: No Contest.

   Sanctions: Formal apology in chapter, staggard for time equal to time out of the house upon return to the house. Recommendation for suspension.

1. February 7, 2012

   Charges: A brother was brought up for conduct unbecoming.

   Plea: Not Responsible.

   Sanctions: Letter of formal apology to those offended, immediate removal from office of Standards Board Justice.

1. January 11, 2015

   Charges: A brother was living outside of the house without permission from the chapter. Plea: No Contest.

   Sanctions: The brother must pay the difference between cost to live in the house and his rent, loss of voting rights, and required to still do house and kitchen details.

1. March 21, 2015

   Charges: Four brothers were planning to live outside of the house without permission from the chapter.

   Plea: No Contest.

   Sanctions: The brothers must remain on the house detail plan, maintain contact with the Scholarship Chair, and their voting rights were revoked.

1. April 26, 2015

   Charges: A brother was planning to live outside of the house without permission from the chapter. Plea: No Contest.

   Sanctions: The brother must complete kitchen details or actively attend study tables at a rate set by the Scholarship Chair.

1. February 28, 2016

   Charges: A brother was planning on living outside the house without permission of the chapter.

   Plea: Not Responsible.

   Sanctions: No repercussions.

1. November 28, 2023

   Charges: A brother was planning on living outside the house without permission from the chapter. Plea: No Contest.

   Sanctions: No sanctions imposed, but if no medical exemption was obtained by the start of the following semester, the brother would be recommended for suspension.

1. November 28, 2023

   Charges: A brother was brought up for conduct unbecoming, specifically as it related to attendance and excuses surrounding chapter, as well as dismissive language used when this issue was trying to be resolved.

   Plea: Not Resonsible.

   Sanctions: The brother was told that they should be in chapter more, and that they should create a plan with the Scholarship Chair to ensure they would be in chapter more the next semester. EC was asked to make a clearer excuse plan that also answered the questions "what constitutes an excuse?" and "what constitutes full attendance at chapter?" in order to prevent future communication issues. For this trial, sanctions were given to the accused and a request was made to EC.

### 2025-02-16 src/articles/article1.qmd
Initialize repository

# Bylaw Structure

## Bylaws as Pertaining to the International Fraternity

1. The Bylaws of Beta Nu Chapter of Theta Chi Fraternity are adopted as provided for in the International Bylaws ([IBL](glossary.qmd#sec-IBL)) of Theta Chi Fraternity (Article V, Section 1).
1. The bylaws of this chapter will be superseded by the [IBL](glossary.qmd#sec-IBL) of Theta Chi Fraternity.

## Amendments

1. All proposed amendments to these Bylaws will specify in the motion that they are amendments.
1. A proposed Amendment may not be voted on unless it has been brought up at least one chapter meeting before or has been available for inspection for at least six days. 
1. A proposed amendment must receive a [supermajority](glossary.qmd#sec-supermajority) vote for ratification.

## Suspension

1. Portions of the bylaws may be suspended by [supermajority](glossary.qmd#sec-supermajority) vote of the chapter.
1. Motions to suspend a portion of the bylaws must contain:
   a. To whom the suspension applies.
   a. The time period during which the suspension applies.
   a. The portion to be suspended.
1. The Executive Council ([EC](glossary.qmd#sec-EC)) may issue an [Executive Edict](glossary.qmd#sec-executive-edict) by [absolute majority](glossary.qmd#sec-absolute-majority) vote in the case of an emergency.
   a. The [Executive Edict](glossary.qmd#sec-executive-edict) will be proposed to the chapter at the next chapter meeting with [quorum](glossary.qmd#sec-quorum) by the Vice President.
   a. The [Executive Edict](glossary.qmd#sec-executive-edict) must be approved by the chapter by a [supermajority](glossary.qmd#sec-supermajority) vote in order for the [Executive Edict](glossary.qmd#sec-executive-edict) to remain in effect after the chapter in which it was voted upon.

## Interpretation

1. [EC](glossary.qmd#sec-EC) will have the power to interpret these Bylaws by an [absolute majority](glossary.qmd#sec-absolute-majority) vote. 2. Any brother may bring [EC](glossary.qmd#sec-EC) Bylaw Interpretation [grievances](glossary.qmd#sec-grievance), in writing, to [EC](glossary.qmd#sec-EC).
   a. All [grievances](glossary.qmd#sec-grievance) brought to [EC](glossary.qmd#sec-EC) will, at all times, be confidential.
   a. The results of the [grievances](glossary.qmd#sec-grievances) will be announced to the chapter at the next chapter meeting.
      i. [EC](glossary.qmd#sec-EC) interpretation is subject to overrule by a [supermajority](glossary.qmd#sec-supermajority) vote of the active chapter. A. Voting to overrule an [EC](glossary.qmd#sec-EC) interpretation of these Bylaws will be done by ballot.

## Glossary

1. All highlighted terms are defined in the Glossary section.
1. The Glossary is a binding section of the bylaws.
1. Amendments to the Glossary will follow the procedure in Article I, Section B.

## Appendices

1. This document will have the following appendices:

   a. [EC](glossary.qmd#sec-EC) Interpretations
      i. Will contain a record of [EC](glossary.qmd#sec-EC) interpretations of the local bylaws.
      i. Interpretations that refer to deprecated parts of the local bylaws may be removed at the discretion of the Vice President.
      i. Items may be added to this appendix by the Vice President.

   a. Standards Rulings
      i. Will contain the choice of trial and results of all Trial Hearings for the purpose of establishing precedent.
      i. All parties will remain anonymous.
      i. Items will be added to this appendix by the Vice President and will include the date that the decision was made.
      i. Items that are over five years old may be removed at the discretion of the Vice President.

   a. Permanent Legislation
      i. Will contain all permanent legislation passed by the chapter.
      i. Upon being passed, permanent legislation will be added to this appendix by the Vice President.
      i. Permanent legislation that is revoked or amended will be removed or changed in this appendix by the Vice President.

1. Appendices may be amended or removed by the chapter in the same manner as amending the bylaws.
   a. Any amendment that is not approved by the chapter by [simple majority](glossary.qmd#sec-simple-majority) will be removed from its appendix.

### 2025-02-16 src/articles/article10.qmd
Initialize repository

# Scholarship

## Scholarship Standards

1. Once per semester, brothers and Candidates will fill out grade release forms.
   a. Grade release forms must be filled out prior to the due date for midterm grades.

1. Brothers on Academic Probation are required to make a grade improvement plan with the Scholarship Chair.
   a. The grade improvement plan will be approved by the Scholarship Chair, the President, and the brother. Failure to follow the grade improvement plan as judged by the Scholarship Chair will result in the brother being brought up for standards.
   a. A brother on Academic Probation is allowed to attend at maximum 3 social events per semester. Their responsibilities for rush are reduced to one third (rounded down) of events. This brother will not be allowed to hold an elected position.

1. Members will be evaluated according to the following criteria:

   a. Any brother with a cumulative Grade Point Average (GPA) of less than 3.0 or an immediately previous semester GPA of less than 3.0 will be placed on Academic Probation until the end of the semester and will be required to attend an Academic Review as described in Article XII, Section K.
      i. The Academic Review must be within the first two weeks of being put on Academic Probation.

   a. If a brother has a midterm progress GPA of less than 3.0, the Scholarship Chair may request the brother to make a grade improvement plan in accordance with Article X, Section A, Item 2a.

   a. If a brother is participating in a program where they do not receive a GPA (e.g. a Co-op) but would otherwise be placed on Academic Probation:
      i. They are not placed on Academic Probation that semester.
      i. The next semester in which they are not participating in such a program, they will be placed on Academic Probation.

## New Member Scholarship

1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
1. New Members will be held to the academic standards in Article X, Section A.
1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
1. A candidate is eligible for initiation if they achieved higher than a 3.0 GPA in the previous semester, or if they have a cumulative GPA of greater than 2.5. Upon receiving a Candidate's GPA, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
   a. First semester freshmen are exempt from this rule.
1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an absolute majority vote by the active chapter.

## Privacy

1. The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the GPA of each brother.
1. All brothers are permitted to know the names of brothers on Academic Probation. 3. All brothers are permitted to know the names of brothers who cannot hold office due to grades.

### 2025-02-16 src/articles/article11.qmd
Initialize repository

# Expectations of Brothers

## Code of Conduct

1. No brother will reveal the secrets of the fraternity to anyone who is not an initiated member of Theta Chi Fraternity.
1. All brothers will obey all federal, state, and local laws.
1. All brothers will obey all University regulations and the Interfraternity Congress (IFC) Constitution and Bylaws.
1. All brothers will obey the International Bylaws (IBL).
1. All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.

## Standards of Brotherhood

1. Financial
   a. Brothers will abide by the financial obligations outlined in Article VI, Section C.

1. Rush
   a. Brothers will attend an amount of Rush events as specified by the Rush Plan.

1. Social
   a. Brothers will attend a majority of social events each semester unless they are on Academic Probation.
   a. Brothers not on Academic Probation will be involved in at least one non-greek campus student organization.

1. Scholarship
   a. Brothers will abide by the scholarship standards described in Article X, Section A. 5. Service
   a. Brothers will complete the service hours assigned to them by the Philanthropy and Service Chair.

1. Chapter events

   a. When an event is declared an official chapter event by Executive Council (EC), all members must attend it unless excused by EC. A missed official chapter event that is not excused will count as an unexcused mandatory event.
      i. Missing a mandatory event without an accepted excuse will count as unexcused.
      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
      i. A brother who has three unexcused mandatory events throughout the semester will be staggard.
      i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
      i. A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the secretary with the possibility of recommendation for suspension.

   a. Brothers will attend chapter meetings as outlined in Article III, Section C.

1. Committees
   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
   a. Brothers will attend assigned committee meetings as outlined in Article V, Section G.

## Considerations for Potential New Members

1. When issuing bids to potential new members, the chapter will take into account their behavior, especially towards non-brothers, and ensure that it is consistent with our expectations of brothers.

### 2025-02-16 src/articles/article12.qmd
Initialize repository

# Standards Board

## Preface

1. This section's purpose is to summarize the Standards Board Hearing Procedures in the International Bylaws (IBL), as well as describing the procedure for Academic Review. For more detailed procedures on Standards Board Trials, refer to IBL Article V, Section 22.

## Purpose

1. To judge infractions of the bylaws and standards of the chapter as well as all other laws and rules brothers must adhere to as defined in IBL Article V, Section 22(a).
1. To run Academic Reviews.

## Membership

1. The composition of Standards Board includes the Vice President as the chair, the Chaplain, and three additional at-large members (IBL Article V, Section 22(b)).
1. The terms of office of the members of Standards Board are outlined in the IBL Article V, Section 22(c). 3. Vacancies should be filled according to IBL Article V, Section 22(g).

## Voting

1. Unless otherwise specified, votes of the board are by simple majority.
1. Quorum of the board consists of ⅘ of its members.
1. The voting members of the board are the Chaplain and the three at-large members (IBL Article V, Section 22(i)).
1. The Vice President may only vote in the case of a tie (IBL Article V, Section 22(i)).

## At-Large Member Removal

1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council (EC) position, that at-large member is immediately removed from office.
1. Any At-Large Member may be removed for the following reasons:
   a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
   a. Failure to maintain confidentiality of all proceedings of the board.\
   a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
   a. At-large members can only be removed by an absolute supermajority vote of the active chapter (IBL Article V, Section 22(e)).

## Accusation Procedure

1. All accusations must be submitted in writing to the Vice President within one month of the most recent violation.
   a. Each accusation must be as detailed as possible including at least the clause of the local bylaws that was violated.
   a. Each accusation must be submitted within one month of the violation.

1. Upon receiving the Accusation, the Vice President will decide whether or not a hearing will take place (IBL Article V, Section 22(j)(2)).
   a. The Vice President may request the First Guard and Second Guard to advise him as to whether or not there should be a hearing.
   a. If the Vice President decides that there will not be a hearing, proceedings will end and no hearing will be held.

1. If there is to be a hearing, the Vice President will then decide whether the hearing will be a Standards Board Hearing or a Chapter Hearing.
   a. The Vice President may not request advice from anyone other than a Chapter Advisor on this matter.
   a. If the accuser and/or accused disagree with the decision of which type of hearing the accusations are brought to, they may appeal the decision.
   a. The appeal will be brought exclusively to the voting members of Standards Board to vote on whether the appeal is valid.
      i. If the appeal is found to be valid, the Vice President's decision on the type of hearing will be overruled.

1. The Vice President will then inform the accuser of the validity of the accusation.

1. If the accusation is found to be without merit, proceedings will end and no hearing will be held.

1. If the Vice President decides there will be a hearing, the Vice President will provide written notification to the accused.
   a. The notification must be given within forty-eight hours of receipt of the accusation.
   a. The notification must include:
      i. The accusations with enough detail to allow the accused to prepare a defense.
      i. The type of hearing taking place.

1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
   a. The possible pleas are responsible plea, not responsible plea, and no contest plea.\
   a. If a plea is not received within the twenty-four hours specified above, a no contest plea will be entered.

1. After a plea is entered, the Vice President will schedule a time and place for the hearing.
   a. The hearing shall occur between 1 and 3 weeks after a plea is entered.
   a. The Vice president will notify the accused and accuser of the time, date, and location of the hearing.
      i. If a Standards Board Hearing is to be held, the Vice President will also notify the Chaplain and the at-large members of Standards Board of the time, date, and location of the hearing.
      i. If a Chapter Hearing is to be held, the Vice President will inform all non-suspended brothers of the active chapter and the Chapter Advisory Board (CAB) of the time, date and location of the hearing.

1. The Vice President will inform EC of the accusation, the accused, and the nature of the complaint at the next EC meeting.

1. Recusal
   a. Members of the board will recuse themselves from the hearing if they feel a conflict of interest exists or they are the accused.
   a. Members of the board may be recused by simple majority vote of the remaining board. The accused, accuser, or a member of the board may call for such a vote.
   a. Members of the Standards Board may recuse themselves. Members of Standards Board, the accused, or accuser may call for a vote to recuse any member of Standards Boardup to the beginning of the trial.
   a. Vacancies due to recusal should be filled in accordance with IBL Article V, Section 22(j)(9)(v) or (vi), as they apply to the situation.

1. If the type of hearing was determined to be a Chapter Hearing, proceed with Article XIII, Section E.

## Hearing Preparation

1. Evidence and a statement by the anonymous accuser will be distributed by the Vice President to all members of the Standards Board between twenty-four and forty-eight hours before the hearing date and time.
1. Witnesses may volunteer to speak on behalf of or against the charges.
   a. The witnesses may volunteer by giving a written message to the Vice President stating their intent to participate and their stance at least three hours before the trial.
1. Witnesses will be advised by the Vice President that they are not to discuss the hearing or the accusation outside of the hearing.
1. Witnesses must remain outside the room until called by the Vice President and leave when dismissed.
1. The dress at the hearing will be informal.
1. The Vice President will call the hearing to order and ask all but the directly related participants to leave the room. The directly related participants are the members of Standards Board as defined in Article XII, Section C, Item 2 and the accused.

## Hearing Method

1. The Vice President reads aloud the charges and ensures that the accused understands the charges.

1. The accused may give an opening statement with a time limit as voted on by the voting members of Standards Board.

1. The accused may then be asked questions by the members of Standards Board and the Chapter Advisor (if he is present) with a time limit as voted on by the voting members of Standards Board.

1. All witnesses will be brought into the room by the Vice President.

1. Witnesses that wish to speak for the charges will be chosen in an order decided by the Vice President to give a statement. The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

1. Witnesses that wish to speak against the charges will be chosen in an order decided by the Vice President to give a statement. The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.

1. All witnesses will be excused by the Vice President.

1. The accused may give a closing statement with a time limit as voted on by the voting members of Standards Board.

1. The Vice President will excuse the accused from the hearing.

1. The voting members of Standards Board will determine if the accused is responsible or not responsible for the accusations brought forth against him.
   a. The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. Any member of Standards Board may recall any witnesses or the accused, if further questions arise. This may be done once per witness. To recall a witness more than once requires a unanimous vote of the voting members of Standards Board.

1. The voting members of Standards Board will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past (as found in Appendix B) may be considered.
   a. The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
   a. The voting members of Standards Board will vote on all sanctions, one at a time.
   a. If the sanction being voted on is temporary suspension for any duration of time, the vote must be unanimous in the affirmative in order to succeed.

1. After the sanctions have been determined, the Vice President will readmit the accused back to the hearing and will announce the sanctions given, if any.

1. The Vice President will then inform the accused of the appeal process.

1. The Vice President will then adjourn the hearing.

## Sanctions

1. The board may issue sanctions within its limited scope. The following are examples of possible sanctions:
   a. Community Service
   a. Cost of repairs
   a. Fines
   a. House Service
   a. Letter of Apology
   a. Removal from an Appointed Position
   a. Recommendation for suspension
   a. Temporary Suspension

1. The Vice President will ensure the completion of sanctions.
   a. If the sanctions are not completed, the Vice President will bring the brother up for standards.

## Appeals

1. The accused may appeal a decision of Standards Board.
   a. Appeals must be submitted within 7 days after receiving written notification of the results of the hearing.
   a. If an appeal is made, the confidentiality of the hearing is waived starting at the next regularly scheduled chapter meeting at which quorum is present.

1. A decision can only be appealed for the following reasons:
   a. The procedure for the hearing was not followed.
   a. New information is discovered that wasn't available at the time of hearing.
   a. The sanction is inappropriate.

1. The appeal will be presented in writing to the Vice President and will state the grounds for the appeal.

1. Appeals will be presented to the active chapter at the next regularly scheduled chapter meeting at which quorum is present.

1. At the next chapter meeting, the appellant will explain the reason for the appeal. The Vice President will then explain the board's decision. Following the statements, the accused will leave the room and a discussion will take place. The chapter may overturn the sanctions with a ¾ vote in the affirmative of all chapter members present and eligible to vote.

1. If the decision is overturned, the chapter may give new sanctions by simple majority vote.

1. After the chapter has voted, the accused brother will be readmitted to the meeting by the Vice President and will be informed of the decision by the Vice President.

1. An appeal may be made only once.

## Academic Review

1. An Academic Review shall be held whenever the Scholarship Chair requests an Academic Review in accordance with the duties of their office.

1. An Academic Review is not a Standards Board Hearing.

1. An Academic Review shall be carried out by the Scholarship Chair and the members of Standards Board.

1. A quorum of Standards Board is required to hold an Academic Review.

1. Attendance of an Academic Review is mandatory for all members of Standards Board and the Scholarship Chair.

1. A member of Standards Board may be recused from an Academic Review under the following circumstances:
   a. Members of the board for whom the Scholarship Chair is requesting a suspension trial will recuse themselves.
   a. Members of Standards Board will recuse themselves if they feel a conflict of interest exists.
   a. Members of Standards Board may be recused by a simple majority vote of the remaining members of Standards Board. The brother under review, the Scholarship Chair, or a member of Standards Board may call for such a vote.

1. Process of an Academic Review

   a. Scheduling:
      i. The Vice President will schedule Academic Reviews.
      i. All Academic Reviews for a semester shall be held at the beginning of the semester at the discretion of the Vice President.
      i. Members of Standards Board of whom the Scholarship Chair has requested an Academic Review will have their Academic Reviews completed before the Academic Reviews of brothers not on Standards Board. If the Scholarship Chair has requested an Academic Review for the Vice President, the Academic Review for the Vice President will happen first.
      i. The Vice President will inform the board, Scholarship Chair, and brothers under review of the day's schedule within three days of the Scholarship Chair requesting academic suspensions.

   b. Preparation:
      i. The brother under review is not required to attend.
      i. Both the brother under review and the Scholarship Chair may provide witnesses and any form of relevant documents, including written statements. If either the brother under review or the Scholarship Chair cannot attend the review, any such documents must be sent to the Vice President along with an order of any witnesses to be called.
      i. The Vice President will call the meeting to order and ask all but unrecused members of the board, the Scholarship Chair, and the brother under review to leave the room.

   c. Method:
      i. The Scholarship Chair and brother under review may give an opening statement, in that order.
      i. The Scholarship Chair may then be asked questions by the brother under review and the board.
      i. The brother under review may then be asked questions by the Scholarship Chair and the board.
      i. The Scholarship Chair and then the brother under review may then present any witnesses or documents. If they are not present, the provided witnesses and documents will be presented in the provided order. After each witness gives a statement, the Scholarship Chair, brother under review, and members of Standards Board may ask questions of the witness. Documents will remain with the Vice President until the conclusion of the review.
      i. The Scholarship Chair and brother under review may give closing statements in that order. vi. The Vice President will excuse the Scholarship Chair and brother under review.
      i. The members of Standards Board will then deliberate. The members of Standards Board may consult any documents and recall any witnesses, the Scholarship Chair, or the brother under review if further questions arise.
      i. The voting members of Standards Board will vote to either recommend the brother under review for suspension, or to not recommend the brother under review for suspension.
      i. The Vice President will recall the Scholarship Chair and the brother under review and inform them of the decision made by Standards Board.
      i. If Standards Board voted to recommend the brother under review for suspension, the Vice President will immediately inform the President of the decision made by Standards Board and request a suspension trial for the brother under review.

1. In the event that Standards Board does not recommend the brother under review for suspension, the proceedings of the review will remain confidential.

1. In the event that the board recommends the brother under review for suspension the proceedings of the review will not be confidential. Any statements by the Scholarship Chair, brother under review, or witnesses, the content of any presented documents, and the nature of the deliberation done by Standards Board may be requested and discussed during the associated suspension trial.

### 2025-02-16 src/articles/article13.qmd
Initialize repository

# Chapter Hearings

## Purpose

1. To judge infractions of the bylaws on a chapter-wide level.

## Leadership

1. The Vice President of the chapter presides over the hearing as Arbiter. If the Vice President is unable to serve or not present, the Chaplain will preside over the hearing as Arbiter.
1. If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing. If this is not possible, the highest position on Executive Council (EC) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.

## Voting

1. Unless otherwise specified, votes during a Chapter Hearing are by simple majority. 2. Every member of the chapter who is present for the hearing is a voting member. 3. The Arbiter will only vote in the case of a tie.
   a. Quorum of the hearing consists of ⅔ of the chapter.

## Accusation Procedure

1. Chapter Hearings can only be started if the Vice President decides that a Standards Board Hearing should become a Chapter Hearing. As such, the accusation procedure in Article XII, Section F should be used.

## Hearing Preparation

1. Evidence will be distributed by the Arbiter between twenty-four and forty-eight hours before the hearing date and time.
1. The dress at the hearing will be informal.
1. Witnesses may volunteer to speak on behalf or against the charges.
   a. The witnesses may volunteer by giving a written message to the Arbiter stating their intent to participate and stance at least three hours before the hearing.\
   a. Witnesses will be advised by the Arbiter that they are not to discuss the hearing or the accusation outside of the hearing.
   a. The Arbiter will call the hearing to order.

## Hearing Procedure

1. The Arbiter reads aloud the charges and plea and ensures that the accused understands the charges and their plea.

1. The accuser may give an opening statement with a time limit as voted on by the chapter.

1. The accused may give an opening statement with a time limit as voted on by the chapter.

1. The accuser may then be asked questions by the chapter with a time limit as voted on by the chapter.

1. The accused may then be asked questions by the chapter with a time limit as voted on by the chapter.

1. All witnesses will be brought into the room by the Arbiter.

1. Witnesses that wish to speak for the charges will be chosen in an order decided by the Arbiter to give a statement. The chapter will ask questions of the witness(es) with a time limit as voted on by the chapter.

1. Witnesses that wish to speak against the charges will be chosen in an order decided by the Arbiter to give a statement. The chapter will ask questions of the witness(es) with a time limit as voted on by the chapter.

1. All witnesses will be excused by the Arbiter.

1. The accuser may give a closing statement with a time limit as voted on by the chapter.

1. The accused may give a closing statement with a time limit as voted on by the chapter.

1. The Arbiter will excuse the accuser and the accused from the hearing.

1. The chapter will then determine whether the accused is responsible or not responsible.

1. The chapter will then determine appropriate sanctions, if any.
   a. Past judicial history of the accused and sanctions given for similar accusations in the past may be considered.
   a. There will be a discussion to determine each specific sanction. After discussion comes to a close, the sanctions decided upon must be passed by a supermajority of present members vote. If the vote is not passed, the chapter will return to discussion.

1. After the verdict and sanctions have been determined the Arbiter will readmit the accused and accuser back to the hearing and will announce the verdict and sanctions given, if any.

1. The Arbiter will then inform the accused of the appeal process.

1. The Arbiter will then adjourn the hearing.

## Sanctions

1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:\
   a. Counseling
   a. Loss of housing status
   a. Loss of voting privileges
   a. Recommendation of Removal from an Elected Position
   a. Recommendation of Suspension
   a. Probation

### 2025-02-16 src/articles/article14.qmd
Initialize repository

# Suspension and Expulsion Trial

## Preface

1. This section's purpose is to summarize the Suspension and Expulsion Procedures in the International Bylaws (IBL). For more detailed procedures, refer to IBL Article VI, Section 13.

## Purpose

1. To determine whether suspension or expulsion is warranted due to violations of their obligation to the Fraternity. These violations include:
   a. Conduct that indicates he is unworthy to represent, bear the name of, or wear the badge of the Fraternity.
   a. A violation of any oaths taken during Ritual.
   a. A violation of the limitations on memberships as detailed in IBL Article VI, Section 12.
   a. Participation in an initiation conducted in violation of IBL Article VI, Section 4(e).
   a. A violation of any financial obligation to the active chapter.

1. Suspension should be imposed in cases where an action that provides a path back to good standing is appropriate.

1. Expulsion should be imposed when misconduct warrants permanently extinguishing the member's association with the Fraternity (e.g due to severity, repetition, or other appropriate grounds).

## Accusation

1. Any collegiate or alumnus member of a chapter may submit an accusation against any other collegiate or alumnus member of that chapter by making a statement of the charges, orally or in writing, privately to the president of the chapter. Each accusation must be as detailed as possible so that the accused may prepare a defense if they so choose.
1. If the accusing member request actions upon the accusation, the president will follow this procedure:
   a. Establish a date, time, and place for the trial, which shall be scheduled as soon as reasonably practicable.
   a. Notify the accused in writing of the date, time, and place of the trial, at least seven days prior to the time the trial is scheduled. The notice must contain the specific charges. If personal service is not possible, the president shall notify the accused in writing, by mail, or similar method resulting in delivery of a receipt to the chapter, at least fourteen days prior to the meeting.
   a. Notify all collegiate members of the active chapter of the date, time, and place of the trial by the fastest means possible.

## Procedure

1. After the meeting is called to order and a quorum is determined to be present, the president shall read the accusations, withholding the name of the accuser. The meeting may proceed whether or not the accused member attends.
1. Witnesses (members or non-members) may be called by any member, including the accused, to testify as to their knowledge of the accusations. Members, including the accused, may ask questions of any witness.
1. The accused has the right to speak on their own behalf. Members may ask questions of the accused.
1. After all witnesses have been heard, the accused shall withdraw from the meeting. Members then ballot upon the motion to suspend and/or expel the accused. The affirmative vote of a simple majority of all collegiate members eligible to vote shall be necessary to sustain a motion to suspend. A ¾ vote of all collegiate members eligible to vote shall be necessary to expel, except for cases in which the accused member is confirmed to have led or participated in hazing, in which case only a simple majority vote of all collegiate members of the active chapter eligible to vote is needed to expel the member.
1. If two or more members have been accused of the same or related conduct and the hearings of the accusations for such members have been scheduled for a single meeting, all accused members shall withdraw from the meeting before members vote on any of the options. No such accused member shall be eligible to vote with respect to a motion relating to any other of the accused.
1. The result of the votes on all resolutions shall be promptly communicated to the accused member, who shall govern themselves accordingly.
1. No record of the proceeding with respect to an accused member shall be retained unless the motion to suspend or expel is sustained.
   a. If the motion to expel is sustained, the chapter shall promptly send International Headquarters (IHQ) a copy of the notice of meeting served; a complete statement of the original accusations and any written response made by the accused; a numerical record of the number of all members eligible to vote, the number of members eligible and present for the vote, and the number of such members voting for the motion; a summary of all evidence submitted by all witnesses; a copy of the minutes of the meeting recording the action of the chapter.
   a. If a motion to suspend is sustained, the chapter shall promptly report the suspension to IHQ.

## Lifting Suspension

1. If the chapter deems that lifting a suspension given by this section is appropriate, the president of the active chapter which imposed the suspension shall receive a petition signed by more than ⅓ of all collegiate members of the chapter seeking to lift the suspension.
1. The president shall call and conduct a meeting in accordance with IBL Article VI, Section 13(b), paragraphs 1 through 7, excluding paragraph 4, and including the first sentence of paragraph 8.
1. The members shall ballot upon a motion to lift the suspension. This motion needs the affirmative vote of at least ½ of all collegiate members of the chapter eligible to vote in order to sustain the motion.

### 2025-02-16 src/articles/article2.qmd
Initialize repository

# Legislation

## Precedence

1. The legislation of this chapter will be superseded by the Theta Chi International Bylaws (IBL), Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.

## Categories and Duration

1. Temporary Legislation:
   a. Must be passed by a simple majority vote.
   a. Expires one year from the date of passage unless a date of expiration is specified.

1. Permanent Legislation:
   a. Must be passed by a simple majority vote.
   a. Remains in effect indefinitely, until revoked or amended as specified below.

1. Emergency Legislation:
   a. Can be passed by a simple majority of those present (even if quorum is not present).
   a. At the next chapter meeting where quorum is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.

1. Executive Edicts:
   a. Must be approved by an absolute majority vote of Executive Council (EC), which immediately puts the edict into effect as legislation.
      i. At the next chapter meeting at which quorum is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation. The chapter must then approve the legislation for the edict to remain in effect.
   a. Supersedes all previous legislation.

1. If the legislation is not proposed as one of the above types, it will be treated as temporary legislation.

## Revoking or Amending

1. The legislation of this chapter may be revoked or amended by a simple majority vote.
1. No legislation can be revoked or amended if quorum is not present with the exception of Emergency Legislation.

### 2025-02-16 src/articles/article3.qmd
Initialize repository

# Chapter Meetings

## Time

1. The active chapter will meet once per week while school is in session, as required by International Bylaws (IBL) Article V, Section 7, Part A.
1. The default time for a chapter meeting will be Sunday at 6:30 PM unless legislated otherwise.

## Excuses

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a simple majority vote of Executive Council (EC).
1. Failure to attend a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.

## Absences

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
1. A brother who has three unexcused absences throughout the semester will be staggard.
1. A brother who has four unexcused absences throughout the semester will be placed on probation until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

## Rules and Regulations

1. All officer reports and communications must be submitted in writing to the Secretary prior to a chapter meeting at a time decided by the Secretary. Emergency reports or communications may be given at the discretion of the presiding officer.
1. No one will leave any chapter meeting unless excused by the presiding officer.
1. Any member whose conduct is unbecoming of a brother may be asked to leave the meeting by the presiding officer.
1. The First Guard will determine and enforce proper dress code at chapter meetings.
1. At the discretion of the First Guard, entrance to chapter meetings will be conducted according to Ritual.
1. No guests will be permitted on the first floor or basement of the house during a chapter meeting or the preparation thereof unless permitted by the chair.
1. There will be no food or drink, with the exception of water in a resealable container, at any chapter meeting, unless the First Guard declares otherwise.
1. Motions that call for a vote require a simple majority in order to be passed, unless the creator of the motion specifies otherwise.

### 2025-02-16 src/articles/article4.qmd
Initialize repository

# Voting

## Voting Overview

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on probation or financial probation are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in Article IV, Section B, or explicitly voted on by simple majority, the method of voting will be by a counted show of hands.

## Procedure

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council (EC) Interpretation of the bylaws (Article I, Section D)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

1. Balloting
   a. The Second Guard and the Chaplain will collect and count the ballots.
   b. The chaplain will confirm the count and repeat the results to the presiding officer.
   c. No brother may count the ballots for a matter related to himself.
   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the ballots.

1. New Members for Initiation
   a. Balloting on New Members for Initiation will be in accordance with the International Bylaws (IBL) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
   b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.

1. Officer Elections
   a. Officers will be elected by simple majority vote.
   b. In the case that no nominee receives a simple majority, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for CAB interviews.

### 2025-02-16 src/articles/article5.qmd
Initialize repository

# Officer Selection and Duties

## Terms of Office

1. All elected offices will have yearly terms.
1. The President will appoint all appointed officers subject to a simple majority vote of the chapter.
1. Appointed positions will have semesterly terms except for Alumni Relations Chair, Community Standards Chair, and Standards Board At-Large Member.
1. The Recruitment Chair and Public Relations Chair will serve from the end of the first Rush Period after election or appointment through the first Rush period after the election or appointment of a new officer.

## Nominations

1. Nominations will be opened at least one week before elections.
1. All members, in order to be eligible for nomination, must be in good standing with the University and the International Fraternity and must not be on financial probation.

## Elections

1. Officers will be elected in accordance with the International Bylaws (IBL) Article V, Section 3.

1. Nominations must be closed in order to elect an officer.

1. For each elected position the election will proceed as such:
   a. For each candidate:
      i. Candidates will be allowed speeches following these rules:
         1\. Other candidates will leave the room.
         1\. Candidates will be allowed not less than three minutes to speak.
      i. The chapter will be allowed to ask the candidate questions following these rules:
         1\. The chapter will be allowed not less than two minutes to question.
         1\. Any time not used by a candidate for his speech will be allowed for questions.
   a. The chapter will discuss the candidates subject to the following rules:
      i. All candidates will leave the room.
      i. The chapter will be allowed not less than five minutes to discuss.
      i. If the candidate is elected by white ballot, this section does not apply.\
   a. Pledges will be allowed to vote in the election in direct exception to the above Article IV, Section A, Item 2.

1. If an elected position should become vacant:
   a. The President will immediately appoint an interim officer, preferably a brother who has held the office before.
   a. Nominations will immediately open for the vacant position, and will close at the next regularly scheduled chapter meeting.
   a. The week following the opening of nominations, elections will proceed as defined above in Article V, Section C.

## Elected Officers and Their Duties

1. President
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph a.
   a. Serves as a liaison between the chapter and the community.
   a. Attends all Interfraternity Congress (IFC) and Greek Life Office functions expected of the President.
   a. Attends all Chapter Advisory Board (CAB) meetings.
   a. Responsible for the overall completion of Community Standards.
   a. A candidate for the position of President must be interviewed by CAB prior to the election. A simple majority vote of CAB may veto that candidate. This veto can be overruled by a supermajority vote of the chapter. Failure for CAB to meet with a candidate prior to elections will be interpreted as CAB waiving their right to interview the candidate.
   a. Serves as a member of Executive Council (EC).
   a. Must live in the house.

1. Vice President
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is responsible for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in Article I, Section F.
   a. Adds EC Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in Article VII, Section C.
   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in Article IX, Section C.
   a. Serves as chair of EC and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee (CCC).\
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in Article V, Section G, Item 3a. o. Must live in the house.

1. Vice President of Health and Safety
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph c.
   a. Plans and oversees a yearly community outreach event regarding health and safety.
   a. Serves as a liaison between the chapter and community health services.
   a. Organizes events on 7 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year.
   a. Maintains house medical kit.
   a. Serves as a member of EC.
   a. Serves as chair of the Health and Safety Committee.
   a. Must live in the house.

1. Secretary
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in Article III, Section C.
   a. Serves as Secretary of EC.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the IBL Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.

1. Treasurer
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and EC.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on financial probation at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in Article VI, Section B.\
   a. Ensures compliance with the General Rules for chapter finances outlined in Article VI, Section A.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the CAB financial advisor, alumni housing corporation financial advisor, and EC no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the CAB financial advisor, alumni housing corporation financial advisor, and EC.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to CAB.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the CAB prior to the election. A simple majority vote of the CAB may veto that candidate. This veto can be overruled by a supermajority vote of the chapter. Failure for CAB to meet with a candidate prior to elections will be interpreted as CAB waiving their right to interview the candidate.
   a. Serves as a member of EC.
   a. Must live in the house.

1. Marshal
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph f.
   a. Will submit a plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
   a. Will reserve a location for initiation.
   a. Will organize a bid acceptance dinner and the bid acceptance ceremony.
   a. Serves as a member of EC.
   a. Must live in the house.

1. Scholarship Chair
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph i.
   a. Performs all duties specified by the Greek Life Office, IFC, and the University.
   a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:\
      i. A plan for the creation of Scholarship contracts for all brothers.
      i. A plan for ensuring the chapter house is an environment conducive to studying.
      i. A plan for providing incentives for academic achievements.
   a. Will present the scholarship program to new members.
   a. Works with the Marshal to promote academic well-being among New Members.
   a. Organizes a formal scholarship dinner to recognize achievement about scholarship within the chapter.
   a. Will arrange at least one program per semester with a speaker who will talk to the chapter about scholarship or an issue relating to scholarship.
   a. Will ensure all brothers are part of at least one non-greek club or activity.
   a. Attends monthly meetings with the Greek Community Educational Consultants in accordance with Case Western Reserve University (CWRU) Greek Community Standards.
   a. Serves as a member of EC.
   a. Must live in the house.

1. Recruitment Chair
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph l.
   a. Assumes responsibility for directing the recruitment process.
   a. Serves as Chair of the Recruitment Committee.
   a. Will run a recruitment workshop each semester.
   a. Will present a Rush calendar to the chapter by Initiation.
   a. Will be responsible for any Rush period that they have planned including those after their term.
   a. Confirms and tracks the attendance of each brother at Rush events (Article XI, Section B, Item 2). h. Serves as a member of EC.
   a. Must live in the house.

1. Chaplain
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph g.
   a. Handles conflict resolution in the chapter.
   a. Organizes and mediates round table discussions on contentious issues between brothers.
   a. Brings elected officers up for standards for failing to perform the position's responsibilities and duties.
   a. Must live in the house.

1. Historian
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph h.
   a. Assists alumni relations chair with the alumni database.\
   a. Ensures that pictures are taken at chapter events.
   a. Will make a yearly scrapbook for the year that they serve, with assistance from the previous historian.
   a. Manages the chapter's online photo and video galleries jointly with the Public Relations Chair.
   a. Works with the house manager to ensure that composites are displayed correctly.
   a. Maintains and updates the photos around the house.
   a. Maintains the chapter museum.

1. First Guard
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph j.
   a. Assists the Marshal in planning and executing initiation and prepares the chapter for it.
   a. Prepares the chapter room for meetings.
   a. Will enforce reasonable dress in the chapter room as stated in Article III, Section D, Item 4.

1. Second Guard
   a. Performs all duties stated in the IBL Article V, Section 6, paragraph k.
   a. Assists the first guard in preparing the chapter room for meetings.

## Appointed Positions

1. Executive Council Member at Large
   a. Must have previously served on EC for a full term.
   a. Must not hold another EC position.
   a. Assists and advises EC.

1. Public Relations Chair
   a. Serves as chair of the Public Relations Committee.
   a. Works with the Public Relations Committee to create PR for the public events of the chapter at the request of other chairs.
   a. Maintains the chapter social media pages and accounts.
   a. Serves as a member of CCC.

1. Social Chair
   a. Organizes social events.
   a. Ensures that all social events run in accordance with all University, Greek Life, IFC, North American Interfraternity Conference (NIC), and IHQ regulations and policies.
   a. Serves as chair of the Social Committee.
   a. Will attend all IFC Social Chair meetings.
   a. Serves as a member of CCC.

1. Alumni Relations Chair\
   a. Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation and sends out the Alumni newsletter before the last day of classes.
   a. Maintains the alumni database.
   a. Serves as chair of the Alumni Relations Committee.
   a. Organizes the Alumni Ceremony at the end of the semester in which they serve.
   a. Plans the annual OX Roast event with the alumni to be held in the fall semester.
   a. Will be appointed after OX Roast to serve until the next OX Roast.
   a. Serves as a member of CCC.

1. Membership Development Chair
   a. Serves as chair of the Membership Development Committee.
   a. Will plan and carry out at least one event or program in each of the following categories:
      i. Professional development
      i. Brotherhood development
      i. Recreation
   a. Serves as a member of CCC.

1. Philanthropy and Service Chair
   a. Serves as chair of the Philanthropy and Service Committee.
   a. Ensures the chapter meets the Greek Life goals for service.
   a. Informs the chapter of service and philanthropy opportunities.
   a. Serves as a member of CCC.

1. House Manager
   a. Will live in the house.
   a. Assumes responsibility for the maintenance of the fraternity residence and surrounding property.
   a. Oversees and assumes responsibility of the fraternity including repair and replacement of equipment.
   a. Creates, implements, and monitors a parking lot program to be approved by the treasurer.

1. Detail Manager
   a. Will pass a house and kitchen detail plan as legislation by the first chapter meeting of the semester in which they serve. The plan must contain provisions for the assessment of fines for delinquency in details.
   a. Assigns weekly house details and weekly kitchen details.
   a. Will be responsible for the direction of all special event details, which may be called at their discretion.

1. Food Steward
   a. Works with a chef or catering service to maintain a brotherhood meal plan.\
   a. Ensures the service chosen for the meal plan is paid for according to the agreement with the chef or catering service.
   a. Must be on the meal plan.
   a. Works with the Detail Manager to keep public areas in the kitchen clean and ensure proper storage of food.
   a. Assigns cabinet and fridge space to in-house brothers.
   a. Must live in the house.

1. Community Standards Chair
   a. Works with respective positions to ensure Community Standards are completed by the fall deadline.

1. Risk Manager
   a. Schedules Students Meeting About Risk and Responsibility Training (SMARRT) or similar presentations at the request of the Greek Life Office.
   a. Ensures compliance with all Greek Life, University, IHQ, and NIC guidelines and policies.
   a. Attends Office of Greek Life risk manager meetings.

1. Diversity, Equity, and Inclusion Chair
   a. Attends all Diversity, Equity, and Inclusion roundtables hosted by the Greek Life Office. 13. Greek Games Chair
   a. Organizes the chapter's participation in Greek Week.
   a. Attends Greek Week Chair meetings sponsored by the Greek Week Steering Committee. c. Appoints brothers to captain Greek Week events.

1. Interfraternity Congress Representative
   a. Represents the chapter at IFC meetings.
   a. Must have been a brother for at least one full semester.

1. Librarian
   a. Sits on the Scholarship Committee.
   a. Manages house library and book collections.

1. Standards Board At-Large Member
   a. Hears and rules on all cases brought before Standards Board as defined in Article XII.
   a. Attends all meetings of Standards Board.
   a. Keeps confidential all matters related to judicial proceedings.
   a. Treats all brothers and New Members fairly, impartially, and consistently.

1. Temporary Chairs
   a. May be appointed by the President to be in charge of specific events. Examples include Damage Chair, Formal Chair, and Master of the Universe.

## Executive Council

1. Membership
   a. EC will be composed of the following:
      i. President
      i. Vice President
      i. Vice President of Health and Safety
      i. Secretary
      i. Treasurer
      i. Marshal
      i. Scholarship Chair
      i. Recruitment Chair
      i. Executive Council Member at Large

1. Purpose, Duties, and Powers
   a. Interprets the bylaws as outlined in Article I, Section D.
   a. Serves as an executive body.
   a. Guides the chapter in emergencies.
   a. Reviews excuses for chapter meetings and other chapter events.
      i. In evaluating excuses, the EC shall adhere to the standards set in the Acceptable Excuses Plan. The Acceptable Excuses Plan shall consist of the following:
         1\. Specifically what is an acceptable excuse, with examples.
         1\. Specifically what is not an acceptable excuse, with examples.
         1\. The number of unexcused absences, missed chapters, and other mandatory events that are allowed per semester before being taken to standards board.
      i. The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
   a. Reviews Requests for Deferment (Article VI, Section D).
   a. Passes Executive Edicts as defined in Article II, Section B, Item 4.
   a. Suspends portions of the Bylaws subject to chapter approval as defined in Article I, Section C.
   a. Reviews appeals to Academic Probation as defined in Article X, Section A.
   a. Meets with respective CAB member once a month.
   a. Appoints appointed positions.

1. Voting
   a. Voting Members
      i. Vice President
      i. Vice President of Health and Safety\
      i. Secretary
      i. Treasurer
      i. Marshal
      i. Recruitment Chair
      i. Scholarship Chair
   a. Quorum will consist of at least five members, at least four of whom must be voting members. c. All votes are decided by an absolute majority of EC.
      i. The President will have a vote in case of a tie.

1. Procedure
   a. EC is chaired by the Vice President.
   a. EC will meet weekly while school is in session.
   a. EC will admit any brother or candidate unless the meeting is declared closed by the Vice President or an absolute majority of EC.
      i. EC may admit any guest to closed EC by an absolute majority vote.
      i. EC meetings will be closed to non-EC members in situations that require discussing private or emergency matters such as Requests for Deferment.
   a. The Vice President will serve as the representative of EC to the chapter.

## Committees

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1\. Alumni Relations Committee and Member Development Committee
         1\. Health and Safety Committee and Scholarship Committee
         1\. Philanthropy and Service Committee and Social Committee
         1\. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1\. Meet at least once every two weeks as directed by their chair.
            a\. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1\. Assist the chair in the discharge of their duties.
         1\. Create a set of goals for the committee at the first meeting of the committee.
         1\. Work toward the goals of the committee.
   b. Operational Committees\
      i. Ad hoc committees
         1\. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1\. Purpose and Duties
            a\. To create a budget for the chapter for the next year pursuant to Article VI, Section B. 2. To examine any financial issues of the chapter.
         1\. Membership
            a\. The Treasurer will serve as chair of the Budget Committee.
            a\. The body of the committee will be selected by the Treasurer.
         1\. Procedure
            a\. The committee will be created and convened during the budgeting process outlined in Article VI, Section B, Item 3.
            a\. The committee may meet at other times to examine the finances of the chapter at the direction of EC.
      i. Committee Chair Committee (CCC)
         1\. Purpose
            a\. To facilitate communication between committee chairs.
            a\. To keep the Vice President informed of committee business.
            a\. To help the Vice President ensure that committees are performing all necessary duties.
         1\. Membership
            a\. The Vice President will serve as the chair of CCC.
            a\. The chairs of all Standard Committees will be members.
            a\. Other brothers may be added to CCC at the Vice President's discretion.
         1\. Procedure
            a\. The committee will meet at least once every two weeks while school is in session. 2. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1\. The Mandatory Bylaw Revision Committee will function in accordance with Article IX, Section C.

1. Every brother must be a member of both of the Standard Committees that belong to the same committee pair.
   a. Brothers that serve as chairs of one Standard Committee must also be on the other Standard Committee in the committee pair.
   a. Brothers may choose to join other committees at their own discretion.
   a. If a brother misses two meetings of any one of their assigned committees without obtaining an approved excuse from that committee's chair, that committee's chair may bring that brother up for standards for behavior unbecoming of a brother.
   a. Committee meetings scheduled less than five days in advance cannot be counted towards the absences above.

### 2025-02-16 src/articles/article6.qmd
Initialize repository

# Finances

## General Rules

1. Two signatures are required on all accounts of the chapter, pursuant to the International Bylaws (IBL), Article V, Section 9, paragraph b.
1. Neither the chapter nor alumni corporation can have or use any form of ATM, debit, credit or money card that is attached to any account of the chapter or alumni corporation.
1. An officer cannot issue a check to himself.
1. All transactions made by the chapter will not utilize a petty-cash system and must be made by check. All transactions made to the chapter will not utilize a petty-cash system for payments exceeding $100.
1. All reimbursements require a receipt.
1. All statements and record books are reconciled monthly.
1. Only the President or Treasurer may sign contracts on behalf of the chapter.

## Budget

1. The Treasurer will present a preliminary budget to the Budget Committee (Article V, Section G, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a supermajority vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (Article V, Section G, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. Safety Margin and Emergency Fund
   a. Any money leftover for the year from the Safety Margin must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council (EC) and the Chapter Advisory Board (CAB).

## Financial Obligations of Members

1. Each brother, New Member, and Alumnus is responsible for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
   a. Any decision regarding this rule will be decided by EC.
1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.

## Deferments

1. If a brother deems that they will be unable to pay their bill by the due date, they may submit a request for deferment.
1. A request for deferment must be submitted to EC by the due date of the bill that is being deferred.
1. A deferment must be approved by a vote of EC or a supermajority vote of the chapter.
1. A brother that is not following the payment plan in their deferment will have their account balance considered past due.
1. Interest on late payments may be charged at the discretion of EC.

## Payment Schedule and Penalties

1. The due date for any bill will be at least two weeks after the date on which the bill was issued and will be before the next bill is to be issued.

1. The chapter may, by unanimous ballot, exempt a brother from payment of any debts owed to the chapter.
   a. The unpaid debt will be divided equally among the other members of the chapter.

1. If the account balance of any brother, New Member, or Alumnus is negative and past due, he will be placed on financial probation unless a deferment has been approved.
   a. A brother placed on financial probation will be fined no more than $20.
   a. A brother on financial probation loses voting rights.
   a. If a brother is on financial probation for more than one week, a suspension trial will be scheduled for him.
   a. The Alumni Corporation and the chapter financial advisor will be notified of any brother placed on financial probation.

1. If a brother has a debt, including deferments, of over $3,000:
   a. EC will vote on whether or not to hold a suspension trial for him after every bill.
   a. The Treasurer will announce the brother's status to the chapter after every bill.
   a. Any receipt forms that the brother submits must be credited against the debt unless EC approves an exception.

## Financial Privacy Section

1. EC and CAB will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).

## Reimbursements

1. A member who would like to obtain a reimbursement needs approval from all of the following:

   a. The chair who controls the budget in question.
      i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
      i. If the chair who controls the budget is also the treasurer, any other member of EC may act as a substitute.

   a. Any other non-treasurer member of EC.

   a. The Treasurer.

1. Reimbursement requests should be submitted no more than two weeks from the date of purchase or arrival (for shipped items), whichever is later.

### 2025-02-16 src/articles/article7.qmd
Initialize repository

# Housing Policies

## Alcohol, Tobacco, and Illegal Substances

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a simple majority vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in Article VII, Section A, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates Article VII, Section A, Item 1, Article VII, Section A, Item 2, Article VII, Section A, Item 3, or Article VII, Section A, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on probation, and becomes staggard
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. Article VII, Section A, Item 1, Article VII, Section A, Item 2, and Article VII, Section A, Item 3 will become null and void upon the downfall of Western Civilization.

## Housing Eligibility

1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws (IBL).
   a. The following brothers are exempt from this policy:
      i. 1st year students
      i. Commuter Students
      i. Those who are married
      i. Those who receive housing as compensation for employment (e.g. Resident Assistants)
      i. Those who are on Co-op, Study Abroad, or a similar program
      i. Those who were ineligible or exempt at the beginning of the school year\
      i. Those with a prohibitive medical condition as approved by Case Western Reserve University (CWRU)

1. The following brothers must live in the chapter house:
   a. President
   a. Vice President
   a. Vice President of Health and Safety
   a. Treasurer
   a. Marshal
   a. Recruitment Chair
   a. Scholarship Chair
   a. House Manager
   a. Food Steward

1. If the Chaplain is not living in the house, one of the ritual keys must be left in the house.

1. Brothers in violation of Article VII, Section B, Item 1 or Article VII, Section B, Item 2 are to be brought up for standards by the Vice President with the possibility of suspension.

1. In order for a brother to move into the house, they must not be on financial probation and must not have a debt to the chapter exceeding $3000, including deferments.
   a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.

1. Brothers living in the house must have a signed housing contract by the due date (Article V, Section D, Item 5l).

1. Alumni will be permitted one year after graduation or status change to live in the house without chapter approval. After that semester, the brother in question must receive a supermajority vote in order to remain in the house.
   a. Alumni must be taking classes at CWRU to live in the house (i.e. as a graduate student).

1. Only a spouse to a brother living in the house and taking classes at CWRU may live in the house during the school year. A spouse meeting the qualifications must receive a supermajority vote of the chapter to live in the house.

1. Active brothers will have priority over all other possible residents for the purposes of living in the house and room assignments, at the discretion of the Vice President.

## Room Assignments

1. If the numbers of brothers eligible to live in the house exceeds the capacity of the house:

   a. Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of the Vice President.
      i. The house may not be dropped below capacity.
      i. If this method would bring the house below capacity:\
         1\. Of the brothers with the highest roster number among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.

   a. If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified roster number will be forced to move out first.
      i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.

1. Any brother applying for a room must have less than $50 debt, including deferments, at the time room assignments are made, lest they become staggard.

1. Room 205 is reserved for the President unless they waive this right.

1. Room assignments will be made by the Vice President following these guidelines:

   a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:
      i. The group with the most brothers, not to exceed the capacity of the room; else
      i. The group of brothers with the greatest number of brothers with squatter's rights for that particular room; else
      i. The group of brothers with the lowest aggregate roster number; else
      i. The group of brothers decided by a mutually acceptable method.

   a. The Vice President will have penultimate authority, beneath the chapter, to assign rooms to the best of their ability in keeping with the guidelines established in Article VII, Section C, Item 4.

### 2025-02-16 src/articles/article8.qmd
Initialize repository

# Awards

## Award Election Procedure

1. For each award that the chapter gives:
   a. Nominations will be opened prior to voting.
   a. Voting will take place after nominations have been closed.
   a. Voting will be done by show of hands.
   a. A brother may vote *No Confidence* if he is not satisfied with any of the nominees.
   a. There will be no discussion between nominations and voting.
   a. If there are less than 4 nominees, the nominee will be elected to receive the award by plurality of voting members present.
   a. Otherwise, there will be a runoff (decided by plurality) between the three nominees that received the highest counts of votes.
   a. If a plurality of votes cast are *No Confidence*, voting will end and no award will be given.

## Specified Awards

1. Brotherhood Award:
   a. Will be awarded to a current brother who best exemplifies the ideals of Theta Chi Fraternity. b. Will be awarded before the end of the Spring Semester.

1. Alumni Service Award:
   a. Will be given to the alumnus who has done the most for the currently active chapter.
   a. Will be given annually at OX Roast.
   a. A plaque will be maintained by the Alumni Relations Committee Chairman that includes the names of the Alumni who have won the award.

1. Dream Girl Award:
   a. Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
   a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
   a. Voting will be done by ballot in direct exception to Article VIII, Section A, Item 1b.

1. Certificate of Appreciation:
   a. May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.\
   a. Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
   a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
   a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
   a. A nominee must receive a supermajority vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
   a. The chapter may give out any number of this award.

1. The chapter may give out any other awards subject to the procedures defined in Article VIII, Section A.

### 2025-02-16 src/articles/article9.qmd
Initialize repository

# Mandatory Chapter Bylaw Revisions

## Purpose

1. To update the contents of the chapter bylaws which might otherwise become inapplicable as well as introducing bylaw amendments, if applicable.
1. To ensure that the chapter repeatedly renews its knowledge of the contents of the chapter bylaws.

## Frequency

1. Mandatory Revisions will be held within 2 years of the previous mandatory revision period.
1. The Vice President may at any time form a committee to review the chapter bylaws using the process of Mandatory Revisions.

## Committee

1. During Mandatory Revisions, a committee chaired by the Vice President will review the Chapter Bylaws.
1. Members of the committee will be selected by the Vice President.
1. The committee will meet weekly unless a majority of members cannot attend or revisions are complete.

## Process

1. The committee will compose a list of amendments.
   a. An item is put on the list if it is deemed mutually acceptable by members of the committee.

1. The committee will bring this list before the chapter as a block of bylaw amendments.

### 2025-02-16 src/glossary.qmd
Initialize repository

# Glossary

## Absolute Majority {#sec-absolute-majority}

A vote of strictly greater than ½ of the entire voting body, counting all brothers, including those not present and including those without voting rights.

## Absolute Supermajority {#sec-absolute-supermajority}

A vote of strictly greater than ⅔ of the entire voting body, counting all brothers, including those not present and including those without voting rights.

## Academic Probation {#sec-academic-probation}

See Article X, Section A, Item 2b. This is a restorative measure, not a punitive measure.

## Attend {#sec-attend}

A brother attends an event if he fulfills the attendance requirements for that event. Attendance requirements are defined at the discretion of the organizer of the event, with a suggested attendance portion being ¾ of the event's total run time.

## Ballot {#sec-ballot}

A secret vote as defined in Article IV, Section B, Item 2.

## Chapter Advisor {#sec-chapter-advisor}

For the purposes of these bylaws, a Chapter Advisor is any alumnus member of the chapter who serves on the Chapter Advisory Board (CAB).

## Community Standards {#sec-community-standards}

The list of requirements set forth by the Greek Life Office at Case Western Reserve University (CWRU) which is to be completed every calendar year, due finally in December.

## Deferment {#sec-deferment}

A payment plan approved by Executive Council (EC) based on a request for deferment and the recommendations of the Treasurer for a brother's debt.

## Executive Edict {#sec-executive-edict}

Legislation implemented in a time of emergency by a supermajority vote of EC. See Article II, Section B, Item 4.

## Financial Probation {#sec-financial-probation}

See Article VI, Section E, Item 3.

## Grade Improvement Plan {#sec-grade-improvement-plan}

A plan made by a brother on Academic Probation with help from the Scholarship Chair to improve his grades.

## Grievance {#sec-grievance}

A request submitted to EC for clarification of the intention of the bylaws. See Article I, Section D, Item 2.

## Informal Dress {#sec-informal-dress}

Any attire that would be reasonably agreed upon to be non-offensive. This consists of, at the very least, socks or closed-toes shoes, a shirt or upper body covering of some kind, and short/pants or a lower body covering of some kind. Shirts with graphics on them are acceptable only insofar as the graphics on them are acceptable. When in doubt, the chair of the current meeting has sole discretion over what is permissible unless stated otherwise in the bylaws or other rules governing the meeting.

## No Contest Plea {#sec-no-contest-plea}

The Accused attests to the truth of the accusation, but believes there are mitigating circumstances surrounding the accusation which exculpate him.

## Not Responsible {#sec-not-responsible}

A ruling that states that the Accused is not culpable for the accusation against him.

## Not Responsible Plea {#sec-not-responsible-plea}

The Accused denies culpability for the accusation.

## Official Chapter Event {#sec-official-chapter-event}

An event that all brothers must attend.

## Plurality {#sec-plurality}

The number of votes cast for a candidate who receives more than any other (this does not necessarily require an absolute majority).

## Probation {#sec-probation}

A brother on probation cannot attend social events and loses his voting rights.

## Quorum {#sec-quorum}

One more than half of the active chapter or the body described.

## Request for Deferment {#sec-request-for-deferment}

A form that includes how much money a brother wishes to defer, the reason a deferment is needed, and a payment plan for the amount deferred.

## Responsible {#sec-responsible}

A ruling that states that the Accused is culpable for the accusation against him.

## Responsible Plea {#sec-responsible-plea}

The Accused admits that he is rightfully accused and agrees to all sanctions given.

## Roster Number {#sec-roster-number}

For the purposes of these bylaws, a brother's roster number starts as the median of the actual roster numbers of his New Member Class.

## Rush Period {#sec-rush-period}

The period of time starting at the beginning of a fall or spring academic semester and ending at the end of the pledging ceremony that same semester.

## Safety Margin {#sec-safety-margin}

A sum of money built into the budget for the chapter which is set aside in case of unexpected expenses. **Scholarship Plan**\
The semesterly legislation created by the Scholarship Chair which is to include scholarship goals for the chapter and means of reaching those goals.

## Simple Majority {#sec-simple-majority}

A vote that, in order to succeed, requires affirmative votes from strictly more than ½ of brothers present and eligible to vote, provided a quorum is present.

## Social Event {#sec-social-event}

Open and closed parties sponsored by the fraternity and any other event given this designation by EC excluding house meals and Rush events. Examples: Mixers, some Greek Week Events, and Formals.

## Special Event Detail {#sec-special-event-detail}

An official chapter event declared by the Detail Manager with a stated objective such as cleaning the house before inspections or a Rush event. The chapter must be given at least twenty-four hours notice of such a session and excuses for the session will be approved by EC.

## Squatter's Rights {#sec-squatter-rights}

The second highest priority given to a brother when deciding housing assignments. A brother has squatter's rights for a room if he is living in that room during the semester in which room assignments are made.

## Staggard {#sec-staggard}

A brother who is staggard loses squatter's rights and has 100 added to his roster number. This effect stacks with itself.

## Supermajority {#sec-supermajority}

A vote that, in order to succeed, requires affirmative votes from strictly more than ⅔ of brothers present and eligible to vote, provided a quorum is present.

# Acronyms

## CAB {#sec-CAB}

Chapter Advisory Board

## CCC {#sec-CCC}

Committee Chair Committee

## CWRU {#sec-CWRU}

Case Western Reserve University

## EC {#sec-EC}

Executive Council

## GPA {#sec-GPA}

Grade Point Average

## IBL {#sec-IBL}

International Bylaws

## IFC {#sec-IFC}

Interfraternity Congress

## IHQ {#sec-IHQ}

International Headquarters

## NIC {#sec-NIC}

North American Interfraternity Conference

## SMARRT {#sec-SMARRT}

Students Meeting About Risk and Responsibility Training

### 2025-02-16 build.sh

@@ -1,0 +1,3 @@
+#!/usr/bin/env bash
+
+nix bundle --experimental-features "nix-command flakes" .#deploy

### 2025-02-16 scripts/glossary.r

@@ -1,0 +1,19 @@
+files <- strsplit(Sys.getenv("QUARTO_PROJECT_INPUT_FILES")[1], "\n")[[1]]
+glossary <- readLines("glossary.qmd")
+terms <- glossary[stringr::str_detect(glossary, "^## ")] |>
+  stringr::str_remove_all("## ") |>
+  stringi::stri_replace_all_regex("\\{*\\}", "")
+print(files)
+
+for (f in files) {
+  if (f != "glossary.qmd") {
+    co <- readLines(f)
+    if (any(stringr::str_detect(co, paste0(terms, collapse = "|")))) {
+      print(f)
+      print(terms)
+      co <- stringi::stri_replace_all_regex(co, paste0("(?<![:#])", terms),
+        paste0("[:", terms, "](/glossary.html#", terms, ")"), vectorize_all = FALSE)
+      writeLines(co, f)
+    }
+  }
+}

### 2025-02-16 build.sh
fix build script

@@ -1,3 +1,3 @@
 #!/usr/bin/env bash
 
-nix bundle --experimental-features "nix-command flakes" .#deploy
+nix build --experimental-features "nix-command flakes" .#deploy

### 2025-02-27 src/articles/article1.qmd
add glossary shortcodes

@@
 
-1. The Bylaws of Beta Nu Chapter of Theta Chi Fraternity are adopted as provided for in the International Bylaws ([IBL](glossary.qmd#sec-IBL)) of Theta Chi Fraternity (Article V, Section 1).
-1. The bylaws of this chapter will be superseded by the [IBL](glossary.qmd#sec-IBL) of Theta Chi Fraternity.
+1. The Bylaws of Beta Nu Chapter of Theta Chi Fraternity are adopted as provided for in the International Bylaws {{< var acronyms.ibl >}} of Theta Chi Fraternity (Article V, Section 1).
+1. The bylaws of this chapter will be superseded by the {{< var acronyms.ibl >}} of Theta Chi Fraternity.
 
@@
 1. A proposed Amendment may not be voted on unless it has been brought up at least one chapter meeting before or has been available for inspection for at least six days. 
-1. A proposed amendment must receive a [supermajority](glossary.qmd#sec-supermajority) vote for ratification.
+1. A proposed amendment must receive a {{< var glossary.supermajority >}} vote for ratification.
 
@@
 
-1. Portions of the bylaws may be suspended by [supermajority](glossary.qmd#sec-supermajority) vote of the chapter.
+1. Portions of the bylaws may be suspended by {{< var glossary.supermajority >}} vote of the chapter.
 1. Motions to suspend a portion of the bylaws must contain:
@@
    a. The portion to be suspended.
-1.
-The Executive Council ([EC](glossary.qmd#sec-EC)) may issue an [Executive Edict](glossary.qmd#sec-executive-edict) by [absolute majority](glossary.qmd#sec-absolute-majority) vote in the case of an emergency.
-   a. The [Executive Edict](glossary.qmd#sec-executive-edict) will be proposed to the chapter at the next chapter meeting with [quorum](glossary.qmd#sec-quorum) by the Vice President.
+1. The Executive Council ({{< var acronyms.ec >}}) may issue an {{< var glossary.executive-edict >}} by {{< var glossary.absolute-majority >}} vote in the case of an emergency.
+   a. The {{< var glossary.executive-edict >}} will be proposed to the chapter at the next chapter meeting with {{< var glossary.quorum >}} by the Vice President.
    a.
-The [Executive Edict](glossary.qmd#sec-executive-edict) must be approved by the chapter by a [supermajority](glossary.qmd#sec-supermajority) vote in order for the [Executive Edict](glossary.qmd#sec-executive-edict) to remain in effect after the chapter in which it was voted upon.
+The {{< var glossary.executive-edict >}} must be approved by the chapter by a {{< var glossary.supermajority >}} vote in order for the {{< var glossary.executive-edict >}} to remain in effect after the chapter in which it was voted upon.
 
@@
 1.
-[EC](glossary.qmd#sec-EC) will have the power to interpret these Bylaws by an [absolute majority](glossary.qmd#sec-absolute-majority) vote.
+{{< var acronyms.ec >}} will have the power to interpret these Bylaws by an {{< var glossary.absolute-majority >}} vote.
 2.
-Any brother may bring [EC](glossary.qmd#sec-EC) Bylaw Interpretation [grievances](glossary.qmd#sec-grievance), in writing, to [EC](glossary.qmd#sec-EC).
-   a. All [grievances](glossary.qmd#sec-grievance) brought to [EC](glossary.qmd#sec-EC) will, at all times, be confidential.
-   a. The results of the [grievances](glossary.qmd#sec-grievances) will be announced to the chapter at the next chapter meeting.
+Any brother may bring {{< var acronyms.ec >}} Bylaw Interpretation {{< var glossary.grievance >}}s, in writing, to {{< var acronyms.ec >}}.
+   a. All {{< var glossary.grievance >}}s brought to {{< var acronyms.ec >}} will, at all times, be confidential.
+   a. The results of the {{< var glossary.grievance >}}s will be announced to the chapter at the next chapter meeting.
       i.
-[EC](glossary.qmd#sec-EC) interpretation is subject to overrule by a [supermajority](glossary.qmd#sec-supermajority) vote of the active chapter.
+{{< var acronyms.ec >}} interpretation is subject to overrule by a {{< var glossary.supermajority >}} vote of the active chapter.
 A.
-Voting to overrule an [EC](glossary.qmd#sec-EC) interpretation of these Bylaws will be done by ballot.
+Voting to overrule an {{< var acronyms.ec >}} interpretation of these Bylaws will be done by ballot.
 
@@
 
-   a. [EC](glossary.qmd#sec-EC) Interpretations
-      i. Will contain a record of [EC](glossary.qmd#sec-EC) interpretations of the local bylaws.
+   a. {{< var acronyms.ec >}} Interpretations
+      i. Will contain a record of {{< var acronyms.ec >}} interpretations of the local bylaws.
       i. Interpretations that refer to deprecated parts of the local bylaws may be removed at the discretion of the Vice President.
@@
 1. Appendices may be amended or removed by the chapter in the same manner as amending the bylaws.
-   a. Any amendment that is not approved by the chapter by [simple majority](glossary.qmd#sec-simple-majority) will be removed from its appendix.
+   a. Any amendment that is not approved by the chapter by {{< var glossary.simple-majority >}} will be removed from its appendix.

### 2025-02-27 src/glossary.py

@@ -1,0 +1,52 @@
+import glob
+from typing import TypedDict
+import yaml
+
+class Item(TypedDict):
+    term: str
+    definition: str
+
+Glossary = list[Item]
+
+def load_glossary(file_path: str) -> Glossary:
+    glossary = []
+    with open(file_path) as stream:
+        try:
+            glossary: Glossary = yaml.safe_load(stream)
+        except yaml.YAMLError as exc:
+            print(exc)
+    return glossary
+
+def get_sec_name(item: Item) -> str:
+    sec_name = "-".join("".join([i for i in item['term'] if i.isalpha() or i == " "]).split(" ")).lower()
+    sec_name += ""
+
+    return sec_name
+
+def generate_glossary(glossary: Glossary, acronyms: Glossary) -> str:
+    glossary_str = "# Glossary\n\n"
+    glossary_str += "\n".join(f"## {item['term']} {"{#sec-"}{get_sec_name(item)}{"}"}\n\n{item['definition']}" for item in glossary)
+    glossary_str += "\n# Acronyms\n\n"
+    glossary_str += "\n".join(f"## {item['term']} {"{#sec-"}{get_sec_name(item)}{"}"}\n\n{item['definition']}\n" for item in acronyms)
+
+    return glossary_str
+
+def generate_env(glossary: Glossary, acronyms: Glossary) -> str:
+    gloss = {}
+    acron = {}
+    for item in glossary:
+        gloss[get_sec_name(item)] = f"[{item['term']}](glossary.qmd#sec-{get_sec_name(item)})"
+
+    for item in acronyms:
+        acron[get_sec_name(item)] = f"[{item['term']}](glossary.qmd#sec-{get_sec_name(item)})"
+
+    return yaml.dump({"glossary": gloss, "acronyms": acron})
+
+glossary = load_glossary("glossary.yaml")
+acronyms = load_glossary("acronyms.yaml")
+
+with open("glossary.qmd", "w") as f:
+    _ = f.write(generate_glossary(glossary, acronyms))
+
+with open("_variables.yml", "a") as f:
+    _ = f.write(generate_env(glossary, acronyms))

### 2025-09-22 src/articles/article10.qmd
Fix glossary

@@
 
-1. Brothers on Academic Probation are required to make a grade improvement plan with the Scholarship Chair.
+1. Brothers on {{< var glossary.academic-probation >}} are required to make a {{< var glossary.grade-improvement-plan >}} with the Scholarship Chair.
    a.
-The grade improvement plan will be approved by the Scholarship Chair, the President, and the brother.
-Failure to follow the grade improvement plan as judged by the Scholarship Chair will result in the brother being brought up for standards.
+The {{< var glossary.grade-improvement-plan >}} will be approved by the Scholarship Chair, the President, and the brother.
+Failure to follow the {{< var glossary.grade-improvement-plan >}} as judged by the Scholarship Chair will result in the brother being brought up for standards.
    a.
-A brother on Academic Probation is allowed to attend at maximum 3 social events per semester.
+A brother on {{< var glossary.academic-probation >}} is allowed to {{< var glossary.attend >}} at maximum 3 {{< var glossary.social-event >}}s per semester.
 Their responsibilities for rush are reduced to one third (rounded down) of events.
@@
    a.
-Any brother with a cumulative Grade Point Average (GPA) of less than 3.0 or an immediately previous semester GPA of less than 3.0 will be placed on Academic Probation until the end of the semester and will be required to attend an Academic Review as described in Article XII, Section K.
-      i. The Academic Review must be within the first two weeks of being put on Academic Probation.
+Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in Article XII, Section K.
+      i. The Academic Review must be within the first two weeks of being put on {{< var glossary.academic-probation >}}.
 
-   a. If a brother has a midterm progress GPA of less than 3.0, the Scholarship Chair may request the brother to make a grade improvement plan in accordance with Article X, Section A, Item 2a.
+   a.
+If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with Article X, Section A, Item 2a.
 
-   a. If a brother is participating in a program where they do not receive a GPA (e.g. a Co-op) but would otherwise be placed on Academic Probation:
-      i. They are not placed on Academic Probation that semester.
-      i. The next semester in which they are not participating in such a program, they will be placed on Academic Probation.
+   a. If a brother is participating in a program where they do not receive a {{< var acronyms.gpa >}} (e.g. a Co-op) but would otherwise be placed on {{< var glossary.academic-probation >}}:
+      i. They are not placed on {{< var glossary.academic-probation >}} that semester.
+      i. The next semester in which they are not participating in such a program, they will be placed on {{< var glossary.academic-probation >}}.
 
@@
 1.
-A candidate is eligible for initiation if they achieved higher than a 3.0 GPA in the previous semester, or if they have a cumulative GPA of greater than 2.5.
-Upon receiving a Candidate's GPA, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
+A candidate is eligible for initiation if they achieved higher than a 3.0 {{< var acronyms.gpa >}} in the previous semester, or if they have a cumulative {{< var acronyms.gpa >}} of greater than 2.5.
+Upon receiving a Candidate's {{< var acronyms.gpa >}}, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
    a. First semester freshmen are exempt from this rule.
 1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
-   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an absolute majority vote by the active chapter.
+   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an {{< var glossary.absolute-majority >}} vote by the active chapter.
 
@@
 
-1. The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the GPA of each brother.
-1. All brothers are permitted to know the names of brothers on Academic Probation. 3. All brothers are permitted to know the names of brothers who cannot hold office due to grades.
+1. The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the {{< var acronyms.gpa >}} of each brother.
+1.
+All brothers are permitted to know the names of brothers on {{< var glossary.academic-probation >}}.
+3.
+All brothers are permitted to know the names of brothers who cannot hold office due to grades.

### 2025-09-22 src/articles/article11.qmd
Fix glossary

@@
 1. All brothers will obey all federal, state, and local laws.
-1. All brothers will obey all University regulations and the Interfraternity Congress (IFC) Constitution and Bylaws.
-1. All brothers will obey the International Bylaws (IBL).
+1. All brothers will obey all University regulations and the Interfraternity Congress ({{< var acronyms.ifc >}}) Constitution and Bylaws.
+1. All brothers will obey the International Bylaws ({{< var acronyms.ibl >}}).
 1. All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.
@@
 1. Rush
-   a. Brothers will attend an amount of Rush events as specified by the Rush Plan.
+   a. Brothers will {{< var glossary.attend >}} an amount of Rush events as specified by the Rush Plan.
 
 1. Social
-   a. Brothers will attend a majority of social events each semester unless they are on Academic Probation.
-   a. Brothers not on Academic Probation will be involved in at least one non-greek campus student organization.
+   a. Brothers will {{< var glossary.attend >}} a majority of {{< var glossary.social-event >}}s each semester unless they are on {{< var glossary.academic-probation >}}.
+   a. Brothers not on {{< var glossary.academic-probation >}} will be involved in at least one non-greek campus student organization.
 
@@
    a.
-When an event is declared an official chapter event by Executive Council (EC), all members must attend it unless excused by EC.
-A missed official chapter event that is not excused will count as an unexcused mandatory event.
+When an event is declared an {{< var glossary.official-chapter-event >}} by Executive Council ({{< var acronyms.ec >}}), all members must {{< var glossary.attend >}} it unless excused by {{< var acronyms.ec >}}.
+A missed {{< var glossary.official-chapter-event >}} that is not excused will count as an unexcused mandatory event.
       i. Missing a mandatory event without an accepted excuse will count as unexcused.
       i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
-      i. A brother who has three unexcused mandatory events throughout the semester will be staggard.
+      i. A brother who has three unexcused mandatory events throughout the semester will be {{< var glossary.staggard >}}.
       i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
@@
 
-   a. Brothers will attend chapter meetings as outlined in Article III, Section C.
+   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in Article III, Section C.
 
@@
    a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
-   a. Brothers will attend assigned committee meetings as outlined in Article V, Section G.
+   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in Article V, Section G.
 

### 2025-09-22 src/articles/article12.qmd
Fix glossary

@@
 1.
-This section's purpose is to summarize the Standards Board Hearing Procedures in the International Bylaws (IBL), as well as describing the procedure for Academic Review.
-For more detailed procedures on Standards Board Trials, refer to IBL Article V, Section 22.
+This section's purpose is to summarize the Standards Board Hearing Procedures in the International Bylaws ({{< var acronyms.ibl >}}), as well as describing the procedure for Academic Review.
+For more detailed procedures on Standards Board Trials, refer to {{< var acronyms.ibl >}} Article V, Section 22.
 
@@
 
-1. To judge infractions of the bylaws and standards of the chapter as well as all other laws and rules brothers must adhere to as defined in IBL Article V, Section 22(a).
+1. To judge infractions of the bylaws and standards of the chapter as well as all other laws and rules brothers must adhere to as defined in {{< var acronyms.ibl >}} Article V, Section 22(a).
 1. To run Academic Reviews.
@@
 
-1. The composition of Standards Board includes the Vice President as the chair, the Chaplain, and three additional at-large members (IBL Article V, Section 22(b)).
-1. The terms of office of the members of Standards Board are outlined in the IBL Article V, Section 22(c). 3. Vacancies should be filled according to IBL Article V, Section 22(g).
+1. The composition of Standards Board includes the Vice President as the chair, the Chaplain, and three additional at-large members ({{< var acronyms.ibl >}} Article V, Section 22(b)).
+1.
+The terms of office of the members of Standards Board are outlined in the {{< var acronyms.ibl >}} Article V, Section 22(c).
+3.
+Vacancies should be filled according to {{< var acronyms.ibl >}} Article V, Section 22(g).
 
@@
 
-1. Unless otherwise specified, votes of the board are by simple majority.
-1. Quorum of the board consists of ⅘ of its members.
-1. The voting members of the board are the Chaplain and the three at-large members (IBL Article V, Section 22(i)).
-1. The Vice President may only vote in the case of a tie (IBL Article V, Section 22(i)).
+1. Unless otherwise specified, votes of the board are by {{< var glossary.simple-majority >}}.
+1. {{< var glossary.quorum >}} of the board consists of ⅘ of its members.
+1. The voting members of the board are the Chaplain and the three at-large members ({{< var acronyms.ibl >}} Article V, Section 22(i)).
+1. The Vice President may only vote in the case of a tie ({{< var acronyms.ibl >}} Article V, Section 22(i)).
 
@@
 
-1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council (EC) position, that at-large member is immediately removed from office.
+1.
+If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council ({{< var acronyms.ec >}}) position, that at-large member is immediately removed from office.
 1. Any At-Large Member may be removed for the following reasons:
@@
    a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
-   a. At-large members can only be removed by an absolute supermajority vote of the active chapter (IBL Article V, Section 22(e)).
+   a. At-large members can only be removed by an {{< var glossary.absolute-supermajority >}} vote of the active chapter ({{< var acronyms.ibl >}} Article V, Section 22(e)).
 
@@
 
-1. Upon receiving the Accusation, the Vice President will decide whether or not a hearing will take place (IBL Article V, Section 22(j)(2)).
+1. Upon receiving the Accusation, the Vice President will decide whether or not a hearing will take place ({{< var acronyms.ibl >}} Article V, Section 22(j)(2)).
    a. The Vice President may request the First Guard and Second Guard to advise him as to whether or not there should be a hearing.
@@
 1. If there is to be a hearing, the Vice President will then decide whether the hearing will be a Standards Board Hearing or a Chapter Hearing.
-   a. The Vice President may not request advice from anyone other than a Chapter Advisor on this matter.
+   a. The Vice President may not request advice from anyone other than a {{< var glossary.chapter-advisor >}} on this matter.
    a. If the accuser and/or accused disagree with the decision of which type of hearing the accusations are brought to, they may appeal the decision.
@@
 1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
-   a. The possible pleas are responsible plea, not responsible plea, and no contest plea.\
-   a. If a plea is not received within the twenty-four hours specified above, a no contest plea will be entered.
+   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.\
+   a. If a plea is not received within the twenty-four hours specified above, a {{< var glossary.no-contest-plea >}} will be entered.
 
@@
       i.
-If a Chapter Hearing is to be held, the Vice President will inform all non-suspended brothers of the active chapter and the Chapter Advisory Board (CAB) of the time, date and location of the hearing.
+If a Chapter Hearing is to be held, the Vice President will inform all non-suspended brothers of the active chapter and the Chapter Advisory Board ({{< var acronyms.cab >}}) of the time, date and location of the hearing.
 
-1. The Vice President will inform EC of the accusation, the accused, and the nature of the complaint at the next EC meeting.
+1. The Vice President will inform {{< var acronyms.ec >}} of the accusation, the accused, and the nature of the complaint at the next {{< var acronyms.ec >}} meeting.
 
@@
    a. Members of the board will recuse themselves from the hearing if they feel a conflict of interest exists or they are the accused.
-   a. Members of the board may be recused by simple majority vote of the remaining board. The accused, accuser, or a member of the board may call for such a vote.
+   a. Members of the board may be recused by {{< var glossary.simple-majority >}} vote of the remaining board. The accused, accuser, or a member of the board may call for such a vote.
    a.
@@
 Members of Standards Board, the accused, or accuser may call for a vote to recuse any member of Standards Boardup to the beginning of the trial.
-   a. Vacancies due to recusal should be filled in accordance with IBL Article V, Section 22(j)(9)(v) or (vi), as they apply to the situation.
+   a. Vacancies due to recusal should be filled in accordance with {{< var acronyms.ibl >}} Article V, Section 22(j)(9)(v) or (vi), as they apply to the situation.
 
@@
 
-1. The accused may then be asked questions by the members of Standards Board and the Chapter Advisor (if he is present) with a time limit as voted on by the voting members of Standards Board.
+1.
+The accused may then be asked questions by the members of Standards Board and the {{< var glossary.chapter-advisor >}} (if he is present) with a time limit as voted on by the voting members of Standards Board.
 
@@
 Witnesses that wish to speak for the charges will be chosen in an order decided by the Vice President to give a statement.
-The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.
+The accused, {{< var glossary.chapter-advisor >}} (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.
 
@@
 Witnesses that wish to speak against the charges will be chosen in an order decided by the Vice President to give a statement.
-The accused, Chapter Advisor (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.
+The accused, {{< var glossary.chapter-advisor >}} (if he is present), and members of the Standards Board will ask questions of the witness(es) with a time limit as voted on by the voting members of Standards Board.
 
@@
 
-1. The voting members of Standards Board will determine if the accused is responsible or not responsible for the accusations brought forth against him.
+1. The voting members of Standards Board will determine if the accused is {{< var glossary.responsible >}} or {{< var glossary.not-responsible >}} for the accusations brought forth against him.
    a.
-The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
+The Vice President and {{< var glossary.chapter-advisor >}} (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
    a.
@@
    a.
-The Vice President and Chapter Advisor (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
+The Vice President and {{< var glossary.chapter-advisor >}} (if one is present) may offer input to this discussion but may not vote in the final decision unless it is a tie, in which case the Vice President will vote to break the tie.
    a. The voting members of Standards Board will vote on all sanctions, one at a time.
@@
    a. Appeals must be submitted within 7 days after receiving written notification of the results of the hearing.
-   a. If an appeal is made, the confidentiality of the hearing is waived starting at the next regularly scheduled chapter meeting at which quorum is present.
+   a. If an appeal is made, the confidentiality of the hearing is waived starting at the next regularly scheduled chapter meeting at which {{< var glossary.quorum >}} is present.
 
@@
 
-1. Appeals will be presented to the active chapter at the next regularly scheduled chapter meeting at which quorum is present.
+1. Appeals will be presented to the active chapter at the next regularly scheduled chapter meeting at which {{< var glossary.quorum >}} is present.
 
@@
 
-1. If the decision is overturned, the chapter may give new sanctions by simple majority vote.
+1. If the decision is overturned, the chapter may give new sanctions by {{< var glossary.simple-majority >}} vote.
 
@@
 
-1. A quorum of Standards Board is required to hold an Academic Review.
+1. A {{< var glossary.quorum >}} of Standards Board is required to hold an Academic Review.
 
@@
    a.
-Members of Standards Board may be recused by a simple majority vote of the remaining members of Standards Board.
+Members of Standards Board may be recused by a {{< var glossary.simple-majority >}} vote of the remaining members of Standards Board.
 The brother under review, the Scholarship Chair, or a member of Standards Board may call for such a vote.
@@
    b. Preparation:
-      i. The brother under review is not required to attend.
+      i. The brother under review is not required to {{< var glossary.attend >}}.
       i.
 Both the brother under review and the Scholarship Chair may provide witnesses and any form of relevant documents, including written statements.
-If either the brother under review or the Scholarship Chair cannot attend the review, any such documents must be sent to the Vice President along with an order of any witnesses to be called.
+If either the brother under review or the Scholarship Chair cannot {{< var glossary.attend >}} the review, any such documents must be sent to the Vice President along with an order of any witnesses to be called.
       i. The Vice President will call the meeting to order and ask all but unrecused members of the board, the Scholarship Chair, and the brother under review to leave the room.

### 2025-09-22 src/articles/article13.qmd
Fix glossary

@@
 If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing.
-If this is not possible, the highest position on Executive Council (EC) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.
+If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.
 
@@
 1.
-Unless otherwise specified, votes during a Chapter Hearing are by simple majority.
+Unless otherwise specified, votes during a Chapter Hearing are by {{< var glossary.simple-majority >}}.
 2.
@@
 The Arbiter will only vote in the case of a tie.
-   a. Quorum of the hearing consists of ⅔ of the chapter.
+   a. {{< var glossary.quorum >}} of the hearing consists of ⅔ of the chapter.
 
@@
 
-1. The chapter will then determine whether the accused is responsible or not responsible.
+1. The chapter will then determine whether the accused is {{< var glossary.responsible >}} or {{< var glossary.not-responsible >}}.
 
@@
 There will be a discussion to determine each specific sanction.
-After discussion comes to a close, the sanctions decided upon must be passed by a supermajority of present members vote.
+After discussion comes to a close, the sanctions decided upon must be passed by a {{< var glossary.supermajority >}} of present members vote.
 If the vote is not passed, the chapter will return to discussion.
@@
    a. Recommendation of Suspension
-   a. Probation
+   a. {{< var glossary.probation >}}

### 2025-09-22 src/articles/article14.qmd
Fix glossary

@@
 
-1. This section's purpose is to summarize the Suspension and Expulsion Procedures in the International Bylaws (IBL). For more detailed procedures, refer to IBL Article VI, Section 13.
+1.
+This section's purpose is to summarize the Suspension and Expulsion Procedures in the International Bylaws ({{< var acronyms.ibl >}}).
+For more detailed procedures, refer to {{< var acronyms.ibl >}} Article VI, Section 13.
 
@@
    a. A violation of any oaths taken during Ritual.
-   a. A violation of the limitations on memberships as detailed in IBL Article VI, Section 12.
-   a. Participation in an initiation conducted in violation of IBL Article VI, Section 4(e).
+   a. A violation of the limitations on memberships as detailed in {{< var acronyms.ibl >}} Article VI, Section 12.
+   a. Participation in an initiation conducted in violation of {{< var acronyms.ibl >}} Article VI, Section 4(e).
    a. A violation of any financial obligation to the active chapter.
@@
 1.
-After the meeting is called to order and a quorum is determined to be present, the president shall read the accusations, withholding the name of the accuser.
-The meeting may proceed whether or not the accused member attends.
+After the meeting is called to order and a {{< var glossary.quorum >}} is determined to be present, the president shall read the accusations, withholding the name of the accuser.
+The meeting may proceed whether or not the accused member {{< var glossary.attend >}}s.
 1.
@@
 After all witnesses have been heard, the accused shall withdraw from the meeting.
-Members then ballot upon the motion to suspend and/or expel the accused.
-The affirmative vote of a simple majority of all collegiate members eligible to vote shall be necessary to sustain a motion to suspend.
-A ¾ vote of all collegiate members eligible to vote shall be necessary to expel, except for cases in which the accused member is confirmed to have led or participated in hazing, in which case only a simple majority vote of all collegiate members of the active chapter eligible to vote is needed to expel the member.
+Members then {{< var glossary.ballot >}} upon the motion to suspend and/or expel the accused.
+The affirmative vote of a {{< var glossary.simple-majority >}} of all collegiate members eligible to vote shall be necessary to sustain a motion to suspend.
+A ¾ vote of all collegiate members eligible to vote shall be necessary to expel, except for cases in which the accused member is confirmed to have led or participated in hazing, in which case only a {{< var glossary.simple-majority >}} vote of all collegiate members of the active chapter eligible to vote is needed to expel the member.
 1.
@@
    a.
-If the motion to expel is sustained, the chapter shall promptly send International Headquarters (IHQ) a copy of the notice of meeting served; a complete statement of the original accusations and any written response made by the accused; a numerical record of the number of all members eligible to vote, the number of members eligible and present for the vote, and the number of such members voting for the motion; a summary of all evidence submitted by all witnesses; a copy of the minutes of the meeting recording the action of the chapter.
-   a. If a motion to suspend is sustained, the chapter shall promptly report the suspension to IHQ.
+If the motion to expel is sustained, the chapter shall promptly send International Headquarters ({{< var acronyms.ihq >}}) a copy of the notice of meeting served; a complete statement of the original accusations and any written response made by the accused; a numerical record of the number of all members eligible to vote, the number of members eligible and present for the vote, and the number of such members voting for the motion; a summary of all evidence submitted by all witnesses; a copy of the minutes of the meeting recording the action of the chapter.
+   a. If a motion to suspend is sustained, the chapter shall promptly report the suspension to {{< var acronyms.ihq >}}.
 
@@
 If the chapter deems that lifting a suspension given by this section is appropriate, the president of the active chapter which imposed the suspension shall receive a petition signed by more than ⅓ of all collegiate members of the chapter seeking to lift the suspension.
-1. The president shall call and conduct a meeting in accordance with IBL Article VI, Section 13(b), paragraphs 1 through 7, excluding paragraph 4, and including the first sentence of paragraph 8.
 1.
-The members shall ballot upon a motion to lift the suspension.
+The president shall call and conduct a meeting in accordance with {{< var acronyms.ibl >}} Article VI, Section 13(b), paragraphs 1 through 7, excluding paragraph 4, and including the first sentence of paragraph 8.
+1.
+The members shall {{< var glossary.ballot >}} upon a motion to lift the suspension.
 This motion needs the affirmative vote of at least ½ of all collegiate members of the chapter eligible to vote in order to sustain the motion.

### 2025-09-22 src/articles/article2.qmd
Fix glossary

@@
 1.
-The legislation of this chapter will be superseded by the Theta Chi International Bylaws (IBL), Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.
+The legislation of this chapter will be superseded by the Theta Chi International Bylaws ({{< var acronyms.ibl >}}), Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.
 
@@
 1. Temporary Legislation:
-   a. Must be passed by a simple majority vote.
+   a. Must be passed by a {{< var glossary.simple-majority >}} vote.
    a. Expires one year from the date of passage unless a date of expiration is specified.
@@
 1. Permanent Legislation:
-   a. Must be passed by a simple majority vote.
+   a. Must be passed by a {{< var glossary.simple-majority >}} vote.
    a. Remains in effect indefinitely, until revoked or amended as specified below.
@@
 1. Emergency Legislation:
-   a. Can be passed by a simple majority of those present (even if quorum is not present).
-   a. At the next chapter meeting where quorum is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.
+   a. Can be passed by a {{< var glossary.simple-majority >}} of those present (even if {{< var glossary.quorum >}} is not present).
+   a. At the next chapter meeting where {{< var glossary.quorum >}} is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.
 
 1. Executive Edicts:
-   a. Must be approved by an absolute majority vote of Executive Council (EC), which immediately puts the edict into effect as legislation.
+   a. Must be approved by an {{< var glossary.absolute-majority >}} vote of Executive Council ({{< var acronyms.ec >}}), which immediately puts the edict into effect as legislation.
       i.
-At the next chapter meeting at which quorum is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation.
+At the next chapter meeting at which {{< var glossary.quorum >}} is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation.
 The chapter must then approve the legislation for the edict to remain in effect.
@@
 
-1. The legislation of this chapter may be revoked or amended by a simple majority vote.
-1. No legislation can be revoked or amended if quorum is not present with the exception of Emergency Legislation.
+1. The legislation of this chapter may be revoked or amended by a {{< var glossary.simple-majority >}} vote.
+1. No legislation can be revoked or amended if {{< var glossary.quorum >}} is not present with the exception of Emergency Legislation.

### 2025-09-22 src/articles/article3.qmd
Fix glossary

@@
 
-1. The active chapter will meet once per week while school is in session, as required by International Bylaws (IBL) Article V, Section 7, Part A.
+1. The active chapter will meet once per week while school is in session, as required by International Bylaws ({{< var acronyms.ibl >}}) Article V, Section 7, Part A.
 1. The default time for a chapter meeting will be Sunday at 6:30 PM unless legislated otherwise.
@@
 1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
-1. Excuses must be approved by a simple majority vote of Executive Council (EC).
-1. Failure to attend a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.
+1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
+1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.
 
@@
 1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
-1. A brother who has three unexcused absences throughout the semester will be staggard.
-1. A brother who has four unexcused absences throughout the semester will be placed on probation until the end of the semester.
+1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
+1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
 1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.
@@
 1. There will be no food or drink, with the exception of water in a resealable container, at any chapter meeting, unless the First Guard declares otherwise.
-1. Motions that call for a vote require a simple majority in order to be passed, unless the creator of the motion specifies otherwise.
+1. Motions that call for a vote require a {{< var glossary.simple-majority >}} in order to be passed, unless the creator of the motion specifies otherwise.

### 2025-09-22 src/articles/article4.qmd
Fix glossary

@@
 1. All brothers eligible to vote must vote.
-1. Only active brothers who are not on probation or financial probation are eligible to vote.
+1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
 1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
 1. A brother not required to pay local dues is ineligible to vote.
-1. Unless specified in Article IV, Section B, or explicitly voted on by simple majority, the method of voting will be by a counted show of hands.
+1. Unless specified in Article IV, Section B, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.
 
@@
    b. Officer Elections
-   c. To overturn an Executive Council (EC) Interpretation of the bylaws (Article I, Section D)
+   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (Article I, Section D)
    d. At a suspension trial
@@
 
-1. Balloting
-   a. The Second Guard and the Chaplain will collect and count the ballots.
+1. {{< var glossary.ballot >}}ing
+   a. The Second Guard and the Chaplain will collect and count the {{< var glossary.ballot >}}s.
    b. The chaplain will confirm the count and repeat the results to the presiding officer.
-   c. No brother may count the ballots for a matter related to himself.
-   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the ballots.
+   c. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
+   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.
 
 1. New Members for Initiation
-   a. Balloting on New Members for Initiation will be in accordance with the International Bylaws (IBL) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
+   a.
+{{< var glossary.ballot >}}ing on New Members for Initiation will be in accordance with the International Bylaws ({{< var acronyms.ibl >}}) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
    b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.
@@
 1. Officer Elections
-   a. Officers will be elected by simple majority vote.
-   b. In the case that no nominee receives a simple majority, there will immediately be another vote between all candidates who received the two highest counts of votes.\
-   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for CAB interviews.
+   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
+   b. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
+   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

### 2025-09-22 src/articles/article5.qmd
Fix glossary

@@
 1. All elected offices will have yearly terms.
-1. The President will appoint all appointed officers subject to a simple majority vote of the chapter.
+1. The President will appoint all appointed officers subject to a {{< var glossary.simple-majority >}} vote of the chapter.
 1. Appointed positions will have semesterly terms except for Alumni Relations Chair, Community Standards Chair, and Standards Board At-Large Member.
 1.
-The Recruitment Chair and Public Relations Chair will serve from the end of the first Rush Period after election or appointment through the first Rush period after the election or appointment of a new officer.
+The Recruitment Chair and Public Relations Chair will serve from the end of the first {{< var glossary.rush-period >}} after election or appointment through the first {{< var glossary.rush-period >}} after the election or appointment of a new officer.
 
@@
 1. Nominations will be opened at least one week before elections.
-1. All members, in order to be eligible for nomination, must be in good standing with the University and the International Fraternity and must not be on financial probation.
+1. All members, in order to be eligible for nomination, must be in good standing with the University and the International Fraternity and must not be on {{< var glossary.financial-probation >}}.
 
@@
 
-1. Officers will be elected in accordance with the International Bylaws (IBL) Article V, Section 3.
+1. Officers will be elected in accordance with the International Bylaws ({{< var acronyms.ibl >}}) Article V, Section 3.
 
@@
       i. Candidates will be allowed speeches following these rules:
-         1\. Other candidates will leave the room.
-         1\. Candidates will be allowed not less than three minutes to speak.
+         1. Other candidates will leave the room.
+         1. Candidates will be allowed not less than three minutes to speak.
       i. The chapter will be allowed to ask the candidate questions following these rules:
-         1\. The chapter will be allowed not less than two minutes to question.
-         1\. Any time not used by a candidate for his speech will be allowed for questions.
+         1. The chapter will be allowed not less than two minutes to question.
+         1. Any time not used by a candidate for his speech will be allowed for questions.
    a. The chapter will discuss the candidates subject to the following rules:
@@
       i. The chapter will be allowed not less than five minutes to discuss.
-      i. If the candidate is elected by white ballot, this section does not apply.\
+      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
    a. Pledges will be allowed to vote in the election in direct exception to the above Article IV, Section A, Item 2.
@@
 1. President
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph a.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph a.
    a. Serves as a liaison between the chapter and the community.
-   a. Attends all Interfraternity Congress (IFC) and Greek Life Office functions expected of the President.
-   a. Attends all Chapter Advisory Board (CAB) meetings.
-   a. Responsible for the overall completion of Community Standards.
+   a. {{< var glossary.attend >}}s all Interfraternity Congress ({{< var acronyms.ifc >}}) and Greek Life Office functions expected of the President.
+   a. {{< var glossary.attend >}}s all Chapter Advisory Board ({{< var acronyms.cab >}}) meetings.
+   a. {{< var glossary.responsible >}} for the overall completion of {{< var glossary.community-standards >}}.
    a.
-A candidate for the position of President must be interviewed by CAB prior to the election.
-A simple majority vote of CAB may veto that candidate.
-This veto can be overruled by a supermajority vote of the chapter.
-Failure for CAB to meet with a candidate prior to elections will be interpreted as CAB waiving their right to interview the candidate.
-   a. Serves as a member of Executive Council (EC).
+A candidate for the position of President must be interviewed by {{< var acronyms.cab >}} prior to the election.
+A {{< var glossary.simple-majority >}} vote of {{< var acronyms.cab >}} may veto that candidate.
+This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter.
+Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
+   a. Serves as a member of Executive Council ({{< var acronyms.ec >}}).
    a. Must live in the house.
@@
 1. Vice President
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph b.
-   a. Serves as Parliamentarian for the chapter and is responsible for all committees.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
+   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
    a. Maintains the chapter's local bylaws.
@@
    a. Adds all permanent legislation to the appropriate appendix as outlined in Article I, Section F.
-   a. Adds EC Interpretations to the Appendices.
+   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
    a. Appoints active members to committees at the beginning of each semester.
    a. Assigns living space as outlined in Article VII, Section C.
-   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
+   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
    a. Serves as chair of the Bylaw Revision Committee as outlined in Article IX, Section C.
-   a. Serves as chair of EC and represents it to the chapter.
-   a. Serves as chair of the Committee Chair Committee (CCC).\
+   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
+   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).\
    a. Serves as chair of Standards Board.
@@
 1. Vice President of Health and Safety
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph c.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph c.
    a. Plans and oversees a yearly community outreach event regarding health and safety.
@@
    a. Maintains house medical kit.
-   a. Serves as a member of EC.
+   a. Serves as a member of {{< var acronyms.ec >}}.
    a. Serves as chair of the Health and Safety Committee.
@@
 1. Secretary
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph d.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
    a. Records attendance and enforces the standards for attendance in Article III, Section C.
-   a. Serves as Secretary of EC.
+   a. Serves as Secretary of {{< var acronyms.ec >}}.
    a. Collects all legislation, Bylaw amendments, and Officer Reports.
-   a. Sets the agenda for chapter meetings according to the IBL Article V, Section 8, paragraph d.
+   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
    a. Maintains the mailbox and mail closet.
@@
 1. Treasurer
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph e.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
    a. Is accountable to the Alumni Corporation.
@@
    a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
-   a. Keeps private all individual account balances except from the brother whose account it is and EC.
+   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
    a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
-   a. Announces the names of all members on financial probation at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
+   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
    a. Will create a budget following the process outlined in Article VI, Section B.\
@@
    a. Will file taxes at least two weeks before the filing deadline each year.
-   a. Will ensure that taxes will be reviewed by the CAB financial advisor, alumni housing corporation financial advisor, and EC no later than one month before the filing deadline.
-   a. Will send taxes by certified mail, and will distribute this certification to the CAB financial advisor, alumni housing corporation financial advisor, and EC.
+   a.
+Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
+   a.
+Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
    a. Will retain a physical and electronic backup of financial records for no fewer than five years.
    a. Maintain a changelog of the budget.
-   a. Give a monthly financial report to the chapter and deliver the report to CAB.
+   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
    a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
@@
    a.
-A candidate for the position of Treasurer must be interviewed by the CAB prior to the election.
-A simple majority vote of the CAB may veto that candidate.
-This veto can be overruled by a supermajority vote of the chapter.
-Failure for CAB to meet with a candidate prior to elections will be interpreted as CAB waiving their right to interview the candidate.
-   a. Serves as a member of EC.
+A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election.
+A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate.
+This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter.
+Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
+   a. Serves as a member of {{< var acronyms.ec >}}.
    a. Must live in the house.
@@
 1. Marshal
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph f.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph f.
    a. Will submit a plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
@@
    a. Will organize a bid acceptance dinner and the bid acceptance ceremony.
-   a. Serves as a member of EC.
+   a. Serves as a member of {{< var acronyms.ec >}}.
    a. Must live in the house.
@@
 1. Scholarship Chair
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph i.
-   a. Performs all duties specified by the Greek Life Office, IFC, and the University.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph i.
+   a. Performs all duties specified by the Greek Life Office, {{< var acronyms.ifc >}}, and the University.
    a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:\
@@
    a. Will ensure all brothers are part of at least one non-greek club or activity.
-   a. Attends monthly meetings with the Greek Community Educational Consultants in accordance with Case Western Reserve University (CWRU) Greek Community Standards.
-   a. Serves as a member of EC.
+   a.
+{{< var glossary.attend >}}s monthly meetings with the Greek Community Educational Consultants in accordance with Case Western Reserve University ({{< var acronyms.cwru >}}) Greek {{< var glossary.community-standards >}}.
+   a. Serves as a member of {{< var acronyms.ec >}}.
    a. Must live in the house.
@@
 1. Recruitment Chair
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph l.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph l.
    a. Assumes responsibility for directing the recruitment process.
@@
    a. Will present a Rush calendar to the chapter by Initiation.
-   a. Will be responsible for any Rush period that they have planned including those after their term.
-   a. Confirms and tracks the attendance of each brother at Rush events (Article XI, Section B, Item 2). h. Serves as a member of EC.
+   a. Will be {{< var glossary.responsible >}} for any {{< var glossary.rush-period >}} that they have planned including those after their term.
+   a. Confirms and tracks the attendance of each brother at Rush events (Article XI, Section B, Item 2). h. Serves as a member of {{< var acronyms.ec >}}.
    a. Must live in the house.
@@
 1. Chaplain
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph g.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph g.
    a. Handles conflict resolution in the chapter.
@@
 1. Historian
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph h.
+   a. Performs all duties stated in the I{{< var acronyms.ibl >}}BL Article V, Section 6, paragraph h.
    a. Assists alumni relations chair with the alumni database.\
@@
 1. First Guard
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph j.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph j.
    a. Assists the Marshal in planning and executing initiation and prepares the chapter for it.
@@
 1. Second Guard
-   a. Performs all duties stated in the IBL Article V, Section 6, paragraph k.
+   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph k.
    a. Assists the first guard in preparing the chapter room for meetings.
@@
 1. Executive Council Member at Large
-   a. Must have previously served on EC for a full term.
-   a. Must not hold another EC position.
-   a. Assists and advises EC.
+   a. Must have previously served on {{< var acronyms.ec >}} for a full term.
+   a. Must not hold another {{< var acronyms.ec >}} position.
+   a. Assists and advises {{< var acronyms.ec >}}.
 
@@
    a. Maintains the chapter social media pages and accounts.
-   a. Serves as a member of CCC.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
 
 1. Social Chair
-   a. Organizes social events.
-   a. Ensures that all social events run in accordance with all University, Greek Life, IFC, North American Interfraternity Conference (NIC), and IHQ regulations and policies.
+   a. Organizes {{< var glossary.social-event >}}s.
+   a.
+Ensures that all {{< var glossary.social-event >}}s run in accordance with all University, Greek Life, {{< var acronyms.ifc >}}, North American Interfraternity Conference ({{< var acronyms.nic >}}), and {{< var acronyms.ihq >}} regulations and policies.
    a. Serves as chair of the Social Committee.
-   a. Will attend all IFC Social Chair meetings.
-   a. Serves as a member of CCC.
+   a. Will {{< var glossary.attend >}} all {{< var acronyms.ifc >}} Social Chair meetings.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
 
@@
    a. Will be appointed after OX Roast to serve until the next OX Roast.
-   a. Serves as a member of CCC.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
 
@@
       i. Recreation
-   a. Serves as a member of CCC.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
 
@@
    a. Informs the chapter of service and philanthropy opportunities.
-   a. Serves as a member of CCC.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
 
@@
    a. Assigns weekly house details and weekly kitchen details.
-   a. Will be responsible for the direction of all special event details, which may be called at their discretion.
+   a. Will be {{< var glossary.responsible >}} for the direction of all {{< var glossary.special-event-detail >}}s, which may be called at their discretion.
 
@@
 1. Community Standards Chair
-   a. Works with respective positions to ensure Community Standards are completed by the fall deadline.
+   a. Works with respective positions to ensure {{< var glossary.community-standards >}} are completed by the fall deadline.
 
 1. Risk Manager
-   a. Schedules Students Meeting About Risk and Responsibility Training (SMARRT) or similar presentations at the request of the Greek Life Office.
-   a. Ensures compliance with all Greek Life, University, IHQ, and NIC guidelines and policies.
-   a. Attends Office of Greek Life risk manager meetings.
+   a. Schedules Students Meeting About Risk and Responsibility Training ({{< var acronyms.smarrt >}}) or similar presentations at the request of the Greek Life Office.
+   a. Ensures compliance with all Greek Life, University, {{< var acronyms.ihq >}}, and {{< var acronyms.nic >}} guidelines and policies.
+   a. {{< var glossary.attend >}}s Office of Greek Life risk manager meetings.
 
 1. Diversity, Equity, and Inclusion Chair
-   a. Attends all Diversity, Equity, and Inclusion roundtables hosted by the Greek Life Office. 13. Greek Games Chair
+   a. {{< var glossary.attend >}}s all Diversity, Equity, and Inclusion roundtables hosted by the Greek Life Office. 13. Greek Games Chair
    a. Organizes the chapter's participation in Greek Week.
-   a. Attends Greek Week Chair meetings sponsored by the Greek Week Steering Committee. c. Appoints brothers to captain Greek Week events.
+   a. {{< var glossary.attend >}}s Greek Week Chair meetings sponsored by the Greek Week Steering Committee. c. Appoints brothers to captain Greek Week events.
 
 1. Interfraternity Congress Representative
-   a. Represents the chapter at IFC meetings.
+   a. Represents the chapter at {{< var acronyms.ifc >}} meetings.
    a. Must have been a brother for at least one full semester.
@@
    a. Hears and rules on all cases brought before Standards Board as defined in Article XII.
-   a. Attends all meetings of Standards Board.
+   a. {{< var glossary.attend >}}s all meetings of Standards Board.
    a. Keeps confidential all matters related to judicial proceedings.
@@
 1. Membership
-   a. EC will be composed of the following:
+   a. {{< var acronyms.ec >}} will be composed of the following:
       i. President
@@
    a. Reviews excuses for chapter meetings and other chapter events.
-      i. In evaluating excuses, the EC shall adhere to the standards set in the Acceptable Excuses Plan. The Acceptable Excuses Plan shall consist of the following:
-         1\. Specifically what is an acceptable excuse, with examples.
-         1\. Specifically what is not an acceptable excuse, with examples.
-         1\. The number of unexcused absences, missed chapters, and other mandatory events that are allowed per semester before being taken to standards board.
+      i. In evaluating excuses, the {{< var acronyms.ec >}} shall adhere to the standards set in the Acceptable Excuses Plan. The Acceptable Excuses Plan shall consist of the following:
+         1. Specifically what is an acceptable excuse, with examples.
+         1. Specifically what is not an acceptable excuse, with examples.
+         1. The number of unexcused absences, missed chapters, and other mandatory events that are allowed per semester before being taken to standards board.
       i.
 The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
-   a. Reviews Requests for Deferment (Article VI, Section D).
-   a. Passes Executive Edicts as defined in Article II, Section B, Item 4.
+   a. Reviews Requests for {{< var glossary.deferment >}} (Article VI, Section D).
+   a. Passes {{< var glossary.executive-edict >}}s as defined in Article II, Section B, Item 4.
    a. Suspends portions of the Bylaws subject to chapter approval as defined in Article I, Section C.
-   a. Reviews appeals to Academic Probation as defined in Article X, Section A.
-   a. Meets with respective CAB member once a month.
+   a. Reviews appeals to {{< var glossary.academic-probation >}} as defined in Article X, Section A.
+   a. Meets with respective {{< var acronyms.cab >}} member once a month.
    a. Appoints appointed positions.
@@
       i. Scholarship Chair
-   a. Quorum will consist of at least five members, at least four of whom must be voting members. c. All votes are decided by an absolute majority of EC.
+   a.
+{{< var glossary.quorum >}} will consist of at least five members, at least four of whom must be voting members.
+c.
+All votes are decided by an {{< var glossary.absolute-majority >}} of {{< var acronyms.ec >}}.
       i. The President will have a vote in case of a tie.
@@
 1. Procedure
-   a. EC is chaired by the Vice President.
-   a. EC will meet weekly while school is in session.
-   a. EC will admit any brother or candidate unless the meeting is declared closed by the Vice President or an absolute majority of EC.
-      i. EC may admit any guest to closed EC by an absolute majority vote.
-      i. EC meetings will be closed to non-EC members in situations that require discussing private or emergency matters such as Requests for Deferment.
-   a. The Vice President will serve as the representative of EC to the chapter.
+   a. {{< var acronyms.ec >}} is chaired by the Vice President.
+   a. {{< var acronyms.ec >}} will meet weekly while school is in session.
+   a. {{< var acronyms.ec >}} will admit any brother or candidate unless the meeting is declared closed by the Vice President or an {{< var glossary.absolute-majority >}} of {{< var acronyms.ec >}}.
+      i. {{< var acronyms.ec >}} may admit any guest to closed {{< var acronyms.ec >}} by an {{< var glossary.absolute-majority >}} vote.
+      i.
+{{< var acronyms.ec >}} meetings will be closed to non-{{< var acronyms.ec >}} members in situations that require discussing private or emergency matters such as Requests for {{< var glossary.deferment >}}.
+   a. The Vice President will serve as the representative of {{< var acronyms.ec >}} to the chapter.
 
@@
       i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
-         1\. Alumni Relations Committee and Member Development Committee
-         1\. Health and Safety Committee and Scholarship Committee
-         1\. Philanthropy and Service Committee and Social Committee
-         1\. Public Relations Committee and Recruitment Committee
+         1. Alumni Relations Committee and Member Development Committee
+         1. Health and Safety Committee and Scholarship Committee
+         1. Philanthropy and Service Committee and Social Committee
+         1. Public Relations Committee and Recruitment Committee
       i. All Standard committees will do the following:
-         1\. Meet at least once every two weeks as directed by their chair.
-            a\. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
-         1\. Assist the chair in the discharge of their duties.
-         1\. Create a set of goals for the committee at the first meeting of the committee.
-         1\. Work toward the goals of the committee.
+         1. Meet at least once every two weeks as directed by their chair.
+            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
+         1. Assist the chair in the discharge of their duties.
+         1. Create a set of goals for the committee at the first meeting of the committee.
+         1. Work toward the goals of the committee.
    b. Operational Committees\
       i. Ad hoc committees
-         1\. The Vice President has the power to make other committees at their discretion.
+         1. The Vice President has the power to make other committees at their discretion.
       i. Budget Committee
-         1\. Purpose and Duties
-            a\. To create a budget for the chapter for the next year pursuant to Article VI, Section B. 2. To examine any financial issues of the chapter.
-         1\. Membership
-            a\. The Treasurer will serve as chair of the Budget Committee.
-            a\. The body of the committee will be selected by the Treasurer.
-         1\. Procedure
-            a\. The committee will be created and convened during the budgeting process outlined in Article VI, Section B, Item 3.
-            a\. The committee may meet at other times to examine the finances of the chapter at the direction of EC.
-      i. Committee Chair Committee (CCC)
-         1\. Purpose
-            a\. To facilitate communication between committee chairs.
-            a\. To keep the Vice President informed of committee business.
-            a\. To help the Vice President ensure that committees are performing all necessary duties.
-         1\. Membership
-            a\. The Vice President will serve as the chair of CCC.
-            a\. The chairs of all Standard Committees will be members.
-            a\. Other brothers may be added to CCC at the Vice President's discretion.
-         1\. Procedure
-            a\. The committee will meet at least once every two weeks while school is in session. 2. The Vice President will evaluate progress toward committee goals.
+         1. Purpose and Duties
+            a. To create a budget for the chapter for the next year pursuant to Article VI, Section B. 2. To examine any financial issues of the chapter.
+         1. Membership
+            a. The Treasurer will serve as chair of the Budget Committee.
+            a. The body of the committee will be selected by the Treasurer.
+         1. Procedure
+            a. The committee will be created and convened during the budgeting process outlined in Article VI, Section B, Item 3.
+            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
+      i. Committee Chair Committee ({{< var acronyms.ccc >}})
+         1. Purpose
+            a. To facilitate communication between committee chairs.
+            a. To keep the Vice President informed of committee business.
+            a. To help the Vice President ensure that committees are performing all necessary duties.
+         1. Membership
+            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
+            a. The chairs of all Standard Committees will be members.
+            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
+         1. Procedure
+            a. The committee will meet at least once every two weeks while school is in session. 2. The Vice President will evaluate progress toward committee goals.
       i. Mandatory Bylaw Revision Committee
-         1\. The Mandatory Bylaw Revision Committee will function in accordance with Article IX, Section C.
+         1. The Mandatory Bylaw Revision Committee will function in accordance with Article IX, Section C.
 

### 2025-09-22 src/articles/article6.qmd
Fix glossary

@@
 
-1. Two signatures are required on all accounts of the chapter, pursuant to the International Bylaws (IBL), Article V, Section 9, paragraph b.
+1. Two signatures are required on all accounts of the chapter, pursuant to the International Bylaws ({{< var acronyms.ibl >}}), Article V, Section 9, paragraph b.
 1. Neither the chapter nor alumni corporation can have or use any form of ATM, debit, credit or money card that is attached to any account of the chapter or alumni corporation.
@@
 The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester.
-The proposal must be approved by a supermajority vote of the chapter.
+The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
    a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
@@
    a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
-1. Any officer with a budget may distribute portions of their budget as they see fit. 5. Safety Margin and Emergency Fund
+1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
    a.
-Any money leftover for the year from the Safety Margin must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved.
-This account is only to be accessed with the vote of Executive Council (EC) and the Chapter Advisory Board (CAB).
+Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved.
+This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).
 
@@
 
-1. Each brother, New Member, and Alumnus is responsible for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
-   a. Any decision regarding this rule will be decided by EC.
+1.
+Each brother, New Member, and Alumnus is {{< var glossary.responsible >}} for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
+   a. Any decision regarding this rule will be decided by {{< var acronyms.ec >}}.
 1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
@@
 
-1. If a brother deems that they will be unable to pay their bill by the due date, they may submit a request for deferment.
-1. A request for deferment must be submitted to EC by the due date of the bill that is being deferred.
-1. A deferment must be approved by a vote of EC or a supermajority vote of the chapter.
-1. A brother that is not following the payment plan in their deferment will have their account balance considered past due.
-1. Interest on late payments may be charged at the discretion of EC.
+1. If a brother deems that they will be unable to pay their bill by the due date, they may submit a request for {{< var glossary.deferment >}}.
+1. A request for {{< var glossary.deferment >}} must be submitted to {{< var acronyms.ec >}} by the due date of the bill that is being deferred.
+1. A {{< var glossary.deferment >}} must be approved by a vote of {{< var acronyms.ec >}} or a {{< var glossary.supermajority >}} vote of the chapter.
+1. A brother that is not following the payment plan in their {{< var glossary.deferment >}} will have their account balance considered past due.
+1. Interest on late payments may be charged at the discretion of {{< var acronyms.ec >}}.
 
@@
 
-1. The chapter may, by unanimous ballot, exempt a brother from payment of any debts owed to the chapter.
+1. The chapter may, by unanimous {{< var glossary.ballot >}}, exempt a brother from payment of any debts owed to the chapter.
    a. The unpaid debt will be divided equally among the other members of the chapter.
 
-1. If the account balance of any brother, New Member, or Alumnus is negative and past due, he will be placed on financial probation unless a deferment has been approved.
-   a. A brother placed on financial probation will be fined no more than $20.
-   a. A brother on financial probation loses voting rights.
-   a. If a brother is on financial probation for more than one week, a suspension trial will be scheduled for him.
-   a. The Alumni Corporation and the chapter financial advisor will be notified of any brother placed on financial probation.
+1.
+If the account balance of any brother, New Member, or Alumnus is negative and past due, he will be placed on {{< var glossary.financial-probation >}} unless a {{< var glossary.deferment >}} has been approved.
+   a. A brother placed on {{< var glossary.financial-probation >}} will be fined no more than $20.
+   a. A brother on {{< var glossary.financial-probation >}} loses voting rights.
+   a. If a brother is on {{< var glossary.financial-probation >}} for more than one week, a suspension trial will be scheduled for him.
+   a. The Alumni Corporation and the chapter financial advisor will be notified of any brother placed on {{< var glossary.financial-probation >}}.
 
-1. If a brother has a debt, including deferments, of over $3,000:
-   a. EC will vote on whether or not to hold a suspension trial for him after every bill.
+1. If a brother has a debt, including {{< var glossary.deferment >}}s, of over $3,000:
+   a. {{< var acronyms.ec >}} will vote on whether or not to hold a suspension trial for him after every bill.
    a. The Treasurer will announce the brother's status to the chapter after every bill.
-   a. Any receipt forms that the brother submits must be credited against the debt unless EC approves an exception.
+   a. Any receipt forms that the brother submits must be credited against the debt unless {{< var acronyms.ec >}} approves an exception.
 
@@
 
-1. EC and CAB will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).
+1.
+{{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).
 
@@
       i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
-      i. If the chair who controls the budget is also the treasurer, any other member of EC may act as a substitute.
+      i. If the chair who controls the budget is also the treasurer, any other member of {{< var acronyms.ec >}} may act as a substitute.
 
-   a. Any other non-treasurer member of EC.
+   a. Any other non-treasurer member of {{< var acronyms.ec >}}.
 

### 2025-09-22 src/articles/article7.qmd
Fix glossary

@@
 1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
-   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a simple majority vote of chapter, may only be stored for a period of twenty-four hours.
+   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
    a.
@@
    a. First Offense – $50 fine
-   a. Second Offense – $75 fine, placed on probation, and becomes staggard
+   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
    a. Third Offense – $100 fine and recommendation for suspension to the chapter
@@
 
-1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws (IBL).
+1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws ({{< var acronyms.ibl >}}).
    a. The following brothers are exempt from this policy:
@@
       i. Those who were ineligible or exempt at the beginning of the school year\
-      i. Those with a prohibitive medical condition as approved by Case Western Reserve University (CWRU)
+      i. Those with a prohibitive medical condition as approved by Case Western Reserve University ({{< var acronyms.cwru >}})
 
@@
 
-1. In order for a brother to move into the house, they must not be on financial probation and must not have a debt to the chapter exceeding $3000, including deferments.
+1.
+In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, including {{< var glossary.deferment >}}s.
    a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.
@@
 Alumni will be permitted one year after graduation or status change to live in the house without chapter approval.
-After that semester, the brother in question must receive a supermajority vote in order to remain in the house.
-   a. Alumni must be taking classes at CWRU to live in the house (i.e. as a graduate student).
+After that semester, the brother in question must receive a {{< var glossary.supermajority >}} vote in order to remain in the house.
+   a. Alumni must be taking classes at {{< var acronyms.cwru >}} to live in the house (i.e. as a graduate student).
 
 1.
-Only a spouse to a brother living in the house and taking classes at CWRU may live in the house during the school year.
-A spouse meeting the qualifications must receive a supermajority vote of the chapter to live in the house.
+Only a spouse to a brother living in the house and taking classes at {{< var acronyms.cwru >}} may live in the house during the school year.
+A spouse meeting the qualifications must receive a {{< var glossary.supermajority >}} vote of the chapter to live in the house.
 
@@
       i. If this method would bring the house below capacity:\
-         1\. Of the brothers with the highest roster number among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.
+         1.
+Of the brothers with the highest {{< var glossary.roster-number >}} among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.
 
@@
 If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
-      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified roster number will be forced to move out first.
+      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
       i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.
 
-1. Any brother applying for a room must have less than $50 debt, including deferments, at the time room assignments are made, lest they become staggard.
+1. Any brother applying for a room must have less than $50 debt, including {{< var glossary.deferment >}}s, at the time room assignments are made, lest they become {{< var glossary.staggard >}}.
 
@@
       i. The group with the most brothers, not to exceed the capacity of the room; else
-      i. The group of brothers with the greatest number of brothers with squatter's rights for that particular room; else
-      i. The group of brothers with the lowest aggregate roster number; else
+      i. The group of brothers with the greatest number of brothers with {{< var glossary.squatters-rights >}} for that particular room; else
+      i. The group of brothers with the lowest aggregate {{< var glossary.roster-number >}}; else
       i. The group of brothers decided by a mutually acceptable method.

### 2025-09-22 src/articles/article8.qmd
Fix glossary

@@
    a. There will be no discussion between nominations and voting.
-   a. If there are less than 4 nominees, the nominee will be elected to receive the award by plurality of voting members present.
-   a. Otherwise, there will be a runoff (decided by plurality) between the three nominees that received the highest counts of votes.
-   a. If a plurality of votes cast are *No Confidence*, voting will end and no award will be given.
+   a. If there are less than 4 nominees, the nominee will be elected to receive the award by {{< var glossary.plurality >}} of voting members present.
+   a. Otherwise, there will be a runoff (decided by {{< var glossary.plurality >}}) between the three nominees that received the highest counts of votes.
+   a. If a {{< var glossary.plurality >}} of votes cast are *No Confidence*, voting will end and no award will be given.
 
@@
    a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
-   a. Voting will be done by ballot in direct exception to Article VIII, Section A, Item 1b.
+   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to Article VIII, Section A, Item 1b.
 
@@
    a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
-   a. A nominee must receive a supermajority vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
+   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
    a. The chapter may give out any number of this award.

### 2025-09-28 src/articles/tag-articles.py
add scripts and fix extension

@@ -1,0 +1,40 @@
+import os
+import re
+import random
+import string
+
+# Constants
+HEADER_PATTERN = re.compile(r'^(## .+?)(\s*\{#.*\})?\s*$')
+TAG_TEMPLATE = ' {#sec-art-%s}'
+ID_LENGTH = 8
+
+def generate_id() -> str:
+    return ''.join(random.choices(string.ascii_uppercase + string.digits, k=ID_LENGTH))
+
+def process_file(filepath):
+    changed = False
+    new_lines = []
+
+    with open(filepath, 'r', encoding='utf-8') as f:
+        for line in f:
+            match = HEADER_PATTERN.match(line)
+            if match:
+                header_text, existing_tag = match.groups()
+                if not existing_tag:
+                    new_tag = TAG_TEMPLATE % generate_id()
+                    line = header_text + new_tag + '\n'
+                    changed = True
+            new_lines.append(line)
+
+    if changed:
+        with open(filepath, 'w', encoding='utf-8') as f:
+            f.writelines(new_lines)
+        print(f"Updated: {filepath}")
+
+def main():
+    for filename in os.listdir('.'):
+        if filename.endswith('.qmd'):
+            process_file(filename)
+
+if __name__ == '__main__':
+    main()

### 2025-09-29 src/articles/article1.qmd
Fix glossary
add scripts and fix extension
fix article linking

@@
-# Bylaw Structure
+# Bylaw Structure {#sec-art-WEX7K9OS}
 
-## Bylaws as Pertaining to the International Fraternity
+## Bylaws as Pertaining to the International Fraternity {#sec-art-5XL0LSV9}
 
@@
 
-## Amendments
+## Amendments {#sec-art-YYQHUMCO}
 
@@
 
-## Suspension
+## Suspension {#sec-art-JKVV6S2J}
 
@@
 
-## Interpretation
+## Interpretation {#sec-art-EXPT5HOU}
 
@@
 A.
-Voting to overrule an {{< var acronyms.ec >}} interpretation of these Bylaws will be done by ballot.
+Voting to overrule an {{< var acronyms.ec >}} interpretation of these Bylaws will be done by {{< var glossary.ballot >}}.
 
-## Glossary
+## Glossary {#sec-art-40HBGT7N}
 
@@
 1. The Glossary is a binding section of the bylaws.
-1. Amendments to the Glossary will follow the procedure in Article I, Section B.
+1. Amendments to the Glossary will follow the procedure in @sec-art-YYQHUMCO.
 
-## Appendices
+## Appendices {#sec-art-Q8OV40FK}
 

### 2025-09-29 src/articles/article10.qmd
fix article linking

@@
-# Scholarship
+# Scholarship {#sec-art-Q7X90PJX}
 
-## Scholarship Standards
+## Scholarship Standards {#sec-art-1UWTGO5I}
 
@@
    a.
-Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in Article XII, Section K.
+Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in @sec-art-HL5IIDEQ.
       i. The Academic Review must be within the first two weeks of being put on {{< var glossary.academic-probation >}}.
@@
    a.
-If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with Article X, Section A, Item 2a.
+If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with @sec-art-1UWTGO5I, Item 2a.
 
@@
 
-## New Member Scholarship
+## New Member Scholarship {#sec-art-IVGCFY89}
 
 1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
-1. New Members will be held to the academic standards in Article X, Section A.
+1. New Members will be held to the academic standards in @sec-art-1UWTGO5I.
 1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
@@
 
-## Privacy
+## Privacy {#sec-art-7UQDJG9B}
 

### 2025-09-29 src/articles/article11.qmd
fix article linking

@@
-# Expectations of Brothers
+# Expectations of Brothers {#sec-art-KJJF9K80}
 
-## Code of Conduct
+## Code of Conduct {#sec-art-0MZB8T3Y}
 
@@
 
-## Standards of Brotherhood
+## Standards of Brotherhood {#sec-art-0ERS31Z3}
 
 1. Financial
-   a. Brothers will abide by the financial obligations outlined in Article VI, Section C.
+   a. Brothers will abide by the financial obligations outlined in @sec-art-VDN0D2P4.
 
@@
 1. Scholarship
-   a. Brothers will abide by the scholarship standards described in Article X, Section A. 5. Service
+   a. Brothers will abide by the scholarship standards described in @sec-art-1UWTGO5I.
+
+1. Service
    a. Brothers will complete the service hours assigned to them by the Philanthropy and Service Chair.
@@
 
-   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in Article III, Section C.
+   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in @sec-art-BUK07FVL.
 
 1. Committees
-   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
-   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in Article V, Section G.
+   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in @sec-art-VI2T9PVL.
+   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in @sec-art-VI2T9PVL.
 
-## Considerations for Potential New Members
+## Considerations for Potential New Members {#sec-art-NH6UEJJ1}
 

### 2025-09-29 src/articles/article13.qmd
fix article linking

@@
-# Chapter Hearings
+# Chapter Hearings {#sec-art-BBVW6A2W}
 
-## Purpose
+## Purpose {#sec-art-ID5CAL25}
 
@@
 
-## Leadership
+## Leadership {#sec-art-314J6G1Q}
 
@@
 If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing.
-If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.
+If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (@sec-art-D3IM05AX, Item 1a) as Arbiter.
 
-## Voting
+## Voting {#sec-art-S4K1I20W}
 
@@
 
-## Accusation Procedure
+## Accusation Procedure {#sec-art-C9QQIOS7}
 
@@
 Chapter Hearings can only be started if the Vice President decides that a Standards Board Hearing should become a Chapter Hearing.
-As such, the accusation procedure in Article XII, Section F should be used.
+As such, the accusation procedure in @sec-art-1D0EJQ7H should be used.
 
-## Hearing Preparation
+## Hearing Preparation {#sec-art-1B4EQ2H6}
 
@@
 
-## Hearing Procedure
+## Hearing Procedure {#sec-art-CD9I5LLX}
 
@@
 
-## Sanctions
+## Sanctions {#sec-art-0CQQ1DK3}
 

### 2025-09-29 src/articles/article4.qmd
fix article linking

@@
-# Voting
+# Voting {#sec-art-D6BOCVLV}
 
-## Voting Overview
+## Voting Overview {#sec-art-GW6C9D29}
 
@@
 1. A brother not required to pay local dues is ineligible to vote.
-1. Unless specified in Article IV, Section B, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.
+1. Unless specified in @sec-art-N8IIFY4C, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.
 
-## Procedure
+## Procedure {#sec-art-N8IIFY4C}
 
@@
    b. Officer Elections
-   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (Article I, Section D)
+   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
    d. At a suspension trial

### 2025-09-29 src/articles/article5.qmd
fix article linking

@@
-# Officer Selection and Duties
+# Officer Selection and Duties {#sec-art-F8LOE4WJ}
 
-## Terms of Office
+## Terms of Office {#sec-art-3MIFLS7V}
 
@@
 
-## Nominations
+## Nominations {#sec-art-NUXDQ4I0}
 
@@
 
-## Elections
+## Elections {#sec-art-3AOCUCRJ}
 
@@
       i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
-   a. Pledges will be allowed to vote in the election in direct exception to the above Article IV, Section A, Item 2.
+   a. Pledges will be allowed to vote in the election in direct exception to the above @sec-art-GW6C9D29, Item 2.
 
@@
    a. Nominations will immediately open for the vacant position, and will close at the next regularly scheduled chapter meeting.
-   a. The week following the opening of nominations, elections will proceed as defined above in Article V, Section C.
+   a. The week following the opening of nominations, elections will proceed as defined above in @sec-art-3AOCUCRJ.
 
-## Elected Officers and Their Duties
+## Elected Officers and Their Duties {#sec-art-YZW2AQAI}
 
@@
    a. Ensures legislation records are up to date.
-   a. Adds all permanent legislation to the appropriate appendix as outlined in Article I, Section F.
+   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
    a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
    a. Appoints active members to committees at the beginning of each semester.
-   a. Assigns living space as outlined in Article VII, Section C.
+   a. Assigns living space as outlined in @sec-art-C89656BJ.
    a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
-   a. Serves as chair of the Bylaw Revision Committee as outlined in Article IX, Section C.
+   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
    a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
@@
    a. Serves as chair of Standards Board.
-   a. May make Ad Hoc Committees at their discretion as defined in Article V, Section G, Item 3a. o. Must live in the house.
+   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.
 
@@
    a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
-   a. Records attendance and enforces the standards for attendance in Article III, Section C.
+   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
    a. Serves as Secretary of {{< var acronyms.ec >}}.
@@
    a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
-   a. Will create a budget following the process outlined in Article VI, Section B.\
-   a. Ensures compliance with the General Rules for chapter finances outlined in Article VI, Section A.
+   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
+   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
    a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
@@
    a. Will be {{< var glossary.responsible >}} for any {{< var glossary.rush-period >}} that they have planned including those after their term.
-   a. Confirms and tracks the attendance of each brother at Rush events (Article XI, Section B, Item 2). h. Serves as a member of {{< var acronyms.ec >}}.
+   a. Confirms and tracks the attendance of each brother at Rush events (@sec-art-0ERS31Z3, Item 2). h. Serves as a member of {{< var acronyms.ec >}}.
    a. Must live in the house.
@@
    a. Prepares the chapter room for meetings.
-   a. Will enforce reasonable dress in the chapter room as stated in Article III, Section D, Item 4.
+   a. Will enforce reasonable dress in the chapter room as stated in @sec-art-8XE7XCGC, Item 4.
 
@@
 
-## Appointed Positions
+## Appointed Positions {#sec-art-QQ786XUW}
 
@@
 1. Standards Board At-Large Member
-   a. Hears and rules on all cases brought before Standards Board as defined in Article XII.
+   a. Hears and rules on all cases brought before Standards Board as defined in @sec-art-IHXJUPV0.
    a. {{< var glossary.attend >}}s all meetings of Standards Board.
@@
 
-## Executive Council
+## Executive Council {#sec-art-D3IM05AX}
 
@@
 1. Purpose, Duties, and Powers
-   a. Interprets the bylaws as outlined in Article I, Section D.
+   a. Interprets the bylaws as outlined in @sec-art-EXPT5HOU.
    a. Serves as an executive body.
@@
 The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
-   a. Reviews Requests for {{< var glossary.deferment >}} (Article VI, Section D).
-   a. Passes {{< var glossary.executive-edict >}}s as defined in Article II, Section B, Item 4.
-   a. Suspends portions of the Bylaws subject to chapter approval as defined in Article I, Section C.
-   a. Reviews appeals to {{< var glossary.academic-probation >}} as defined in Article X, Section A.
+   a. Reviews Requests for {{< var glossary.deferment >}} (@sec-art-OUD16M61).
+   a. Passes {{< var glossary.executive-edict >}}s as defined in @sec-art-9HMJ9WUB, Item 4.
+   a. Suspends portions of the Bylaws subject to chapter approval as defined in @sec-art-JKVV6S2J.
+   a. Reviews appeals to {{< var glossary.academic-probation >}} as defined in @sec-art-1UWTGO5I.
    a. Meets with respective {{< var acronyms.cab >}} member once a month.
@@
 
-## Committees
+## Committees {#sec-art-VI2T9PVL}
 
@@
          1. Purpose and Duties
-            a. To create a budget for the chapter for the next year pursuant to Article VI, Section B. 2. To examine any financial issues of the chapter.
+            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
+            a. To examine any financial issues of the chapter.
          1. Membership
@@
          1. Procedure
-            a. The committee will be created and convened during the budgeting process outlined in Article VI, Section B, Item 3.
+            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
             a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
@@
          1. Procedure
-            a. The committee will meet at least once every two weeks while school is in session. 2. The Vice President will evaluate progress toward committee goals.
+            a. The committee will meet at least once every two weeks while school is in session.
+            a. The Vice President will evaluate progress toward committee goals.
       i. Mandatory Bylaw Revision Committee
-         1. The Mandatory Bylaw Revision Committee will function in accordance with Article IX, Section C.
+         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.
 

### 2025-09-29 src/articles/article6.qmd
fix article linking

@@
-# Finances
+# Finances {#sec-art-NV6E374B}
 
-## General Rules
+## General Rules {#sec-art-SKY8T9UM}
 
@@
 
-## Budget
+## Budget {#sec-art-GD7C1K2U}
 
-1. The Treasurer will present a preliminary budget to the Budget Committee (Article V, Section G, Item 2c) no later than six weeks before the beginning of the Fall Semester.
+1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c) no later than six weeks before the beginning of the Fall Semester.
 1.
@@
 1. Budget Committee
-   a. The Budget Committee (Article V, Section G, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
+   a. The Budget Committee (@sec-art-VI2T9PVL, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
    a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
@@
 
-## Financial Obligations of Members
+## Financial Obligations of Members {#sec-art-VDN0D2P4}
 
@@
 
-## Deferments
+## Deferments {#sec-art-OUD16M61}
 
@@
 
-## Payment Schedule and Penalties
+## Payment Schedule and Penalties {#sec-art-1ATKL12C}
 
@@
 
-## Financial Privacy Section
+## Financial Privacy Section {#sec-art-KK0JMIWX}
 
@@
 
-## Reimbursements
+## Reimbursements {#sec-art-FCOCY19N}
 

### 2025-09-29 src/articles/article8.qmd
fix article linking

@@
-# Awards
+# Awards {#sec-art-KAF5NVBG}
 
-## Award Election Procedure
+## Award Election Procedure {#sec-art-WWI418WD}
 
@@
 
-## Specified Awards
+## Specified Awards {#sec-art-GZYYZN72}
 
@@
    a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
-   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to Article VIII, Section A, Item 1b.
+   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to @sec-art-WWI418WD, Item 1b.
 
@@
    a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
-   a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
-   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
+   a. Discussion will be allowed for this award in direct exception to @sec-art-WWI418WD, Item 1c.
+   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to @sec-art-WWI418WD, Item 1b.
    a. The chapter may give out any number of this award.
 
-1. The chapter may give out any other awards subject to the procedures defined in Article VIII, Section A.
+1. The chapter may give out any other awards subject to the procedures defined in @sec-art-WWI418WD.

### 2025-09-29 src/articles/tag-articles.py

@@ -4,7 +4,7 @@ import random
 import string
 
 # Constants
-HEADER_PATTERN = re.compile(r'^(## .+?)(\s*\{#.*\})?\s*$')
+HEADER_PATTERN = re.compile(r'^(##? .+?)(\s*\{#.*\})?\s*$')
 TAG_TEMPLATE = ' {#sec-art-%s}'
 ID_LENGTH = 8
 

### 2025-09-29 src/appendices/appendix2.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

@@
 
-   Charges: A brother was under a 2.2 GPA for two consecutive semesters.
+   Charges: A brother was under a 2.2 {{< var acronyms.gpa >}} for two consecutive semesters.
 
@@
 
-   Sanctions: Recommendation for suspension, voting privileges suspended until off of academic probation.
+   Sanctions: Recommendation for suspension, voting privileges suspended until off of {{< var glossary.academic-probation >}}.
 
@@
 
-   Charges: A brother was under a 2.2 GPA for two consecutive semesters. Brother was currently on co-op.
+   Charges: A brother was under a 2.2 {{< var acronyms.gpa >}} for two consecutive semesters. Brother was currently on co-op.
 
@@
 
-   Sanctions: Formal apology in chapter, staggard for time equal to time out of the house upon return to the house. Recommendation for suspension.
+   Sanctions: Formal apology in chapter, {{< var glossary.staggard >}} for time equal to time out of the house upon return to the house. Recommendation for suspension.
 
@@
 
-   Sanctions: The brother must complete kitchen details or actively attend study tables at a rate set by the Scholarship Chair.
+   Sanctions: The brother must complete kitchen details or actively {{< var glossary.attend >}} study tables at a rate set by the Scholarship Chair.
 
@@
    Sanctions: The brother was told that they should be in chapter more, and that they should create a plan with the Scholarship Chair to ensure they would be in chapter more the next semester.
-EC was asked to make a clearer excuse plan that also answered the questions "what constitutes an excuse?" and "what constitutes full attendance at chapter?" in order to prevent future communication issues.
-For this trial, sanctions were given to the accused and a request was made to EC.
+{{< var acronyms.ec >}} was asked to make a clearer excuse plan that also answered the questions "what constitutes an excuse?" and "what constitutes full attendance at chapter?" in order to prevent future communication issues.
+For this trial, sanctions were given to the accused and a request was made to {{< var acronyms.ec >}}.

### 2025-09-29 src/articles/article12.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

@@
-# Standards Board
+# Standards Board {#sec-art-IHXJUPV0}
 
-## Preface
+## Preface {#sec-art-22W5QO3O}
 
@@
 
-## Purpose
+## Purpose {#sec-art-W45W9VZK}
 
@@
 
-## Membership
+## Membership {#sec-art-31029HI0}
 
@@
 
-## Voting
+## Voting {#sec-art-1U1T2P1X}
 
@@
 
-## At-Large Member Removal
+## At-Large Member Removal {#sec-art-D83OGG9V}
 
@@
 
-## Accusation Procedure
+## Accusation Procedure {#sec-art-1D0EJQ7H}
 
@@
 
-1. If the type of hearing was determined to be a Chapter Hearing, proceed with Article XIII, Section E.
+1. If the type of hearing was determined to be a Chapter Hearing, proceed with @sec-art-1B4EQ2H6.
 
-## Hearing Preparation
+## Hearing Preparation {#sec-art-HEKXL782}
 
@@
 The Vice President will call the hearing to order and ask all but the directly related participants to leave the room.
-The directly related participants are the members of Standards Board as defined in Article XII, Section C, Item 2 and the accused.
+The directly related participants are the members of Standards Board as defined in @sec-art-31029HI0C, Item 2 and the accused.
 
-## Hearing Method
+## Hearing Method {#sec-art-L96ICVPJ}
 
@@
 
-## Sanctions
+## Sanctions {#sec-art-S2YKROAM}
 
@@
 
-## Appeals
+## Appeals {#sec-art-EM09V7RF}
 
@@
 
-## Academic Review
+## Academic Review {#sec-art-HL5IIDEQ}
 

### 2025-09-29 src/articles/article3.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

@@
-# Chapter Meetings
+# Chapter Meetings {#sec-art-R50R4PX6}
 
-## Time
+## Time {#sec-art-386EGZU4}
 
@@
 
-## Excuses
+## Excuses {#sec-art-H23EB4B2}
 
@@
 1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
-1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.
+1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with @sec-art-H23EB4B2, Item 1) will count as an unexcused absence.
 
-## Absences
+## Absences {#sec-art-BUK07FVL}
 
@@
 
-## Rules and Regulations
+## Rules and Regulations {#sec-art-8XE7XCGC}
 

### 2025-09-29 src/articles/article7.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

@@
-# Housing Policies
+# Housing Policies {#sec-art-N4XGGHCH}
 
-## Alcohol, Tobacco, and Illegal Substances
+## Alcohol, Tobacco, and Illegal Substances {#sec-art-6GSVIPRZ}
 
@@
 Alcohol manufactured for the sole sake of cooking (i.e.
-modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in Article VII, Section A, Item 2a, may be stored indefinitely.
+modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in @sec-art-6GSVIPRZ, Item 2a, may be stored indefinitely.
 1. Tobacco may not be possessed and chewed within the house or on the chapter property.
@@
 1.
-If a brother or their guest violates Article VII, Section A, Item 1, Article VII, Section A, Item 2, Article VII, Section A, Item 3, or Article VII, Section A, Item 4, they will be brought up for standards by the President, with sanctions not less than:
+If a brother or their guest violates @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, @sec-art-6GSVIPRZ, Item 3, or @sec-art-6GSVIPRZ, Item 4, they will be brought up for standards by the President, with sanctions not less than:
    a. First Offense – $50 fine
@@
 1. No candles will be burned inside the house or on the chapter property.
-1. Article VII, Section A, Item 1, Article VII, Section A, Item 2, and Article VII, Section A, Item 3 will become null and void upon the downfall of Western Civilization.
+1. @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, and @sec-art-6GSVIPRZ, Item 3 will become null and void upon the downfall of Western Civilization.
 
-## Housing Eligibility
+## Housing Eligibility {#sec-art-71TPHUXH}
 
@@
 
-1. Brothers in violation of Article VII, Section B, Item 1 or Article VII, Section B, Item 2 are to be brought up for standards by the Vice President with the possibility of suspension.
+1. Brothers in violation of @sec-art-71TPHUXH, Item 1 or @sec-art-71TPHUXH, Item 2 are to be brought up for standards by the Vice President with the possibility of suspension.
 
@@
 
-1. Brothers living in the house must have a signed housing contract by the due date (Article V, Section D, Item 5l).
+1. Brothers living in the house must have a signed housing contract by the due date (@sec-art-YZW2AQAI, Item 5l).
 
@@
 
-## Room Assignments
+## Room Assignments {#sec-art-C89656BJ}
 
@@
    a.
-If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
+If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
       i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
-      i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.
+      i. Brothers listed in @sec-art-71TPHUXH, Item 2 cannot be forced to live out of the house.
 
@@
 
-   a.
-The Vice President will have penultimate authority, beneath the chapter, to assign rooms to the best of their ability in keeping with the guidelines established in Article VII, Section C, Item 4.
+   a. The Vice President will have penultimate authority, beneath the chapter, to assign rooms to the best of their ability in keeping with the guidelines established in @sec-art-C89656BJ, Item 4.

### 2025-09-29 scripts/glossary.r

@@ -1,19 +1,0 @@
-files <- strsplit(Sys.getenv("QUARTO_PROJECT_INPUT_FILES")[1], "\n")[[1]]
-glossary <- readLines("glossary.qmd")
-terms <- glossary[stringr::str_detect(glossary, "^## ")] |>
-  stringr::str_remove_all("## ") |>
-  stringi::stri_replace_all_regex("\\{*\\}", "")
-print(files)
-
-for (f in files) {
-  if (f != "glossary.qmd") {
-    co <- readLines(f)
-    if (any(stringr::str_detect(co, paste0(terms, collapse = "|")))) {
-      print(f)
-      print(terms)
-      co <- stringi::stri_replace_all_regex(co, paste0("(?<![:#])", terms),
-        paste0("[:", terms, "](/glossary.html#", terms, ")"), vectorize_all = FALSE)
-      writeLines(co, f)
-    }
-  }
-}

### 2025-09-29 src/articles/tag-articles.py

@@ -1,0 +1,40 @@
+import os
+import re
+import random
+import string
+
+# Constants
+HEADER_PATTERN = re.compile(r'^(##? .+?)(\s*\{#.*\})?\s*$')
+TAG_TEMPLATE = ' {#sec-art-%s}'
+ID_LENGTH = 8
+
+def generate_id() -> str:
+    return ''.join(random.choices(string.ascii_uppercase + string.digits, k=ID_LENGTH))
+
+def process_file(filepath):
+    changed = False
+    new_lines = []
+
+    with open(filepath, 'r', encoding='utf-8') as f:
+        for line in f:
+            match = HEADER_PATTERN.match(line)
+            if match:
+                header_text, existing_tag = match.groups()
+                if not existing_tag:
+                    new_tag = TAG_TEMPLATE % generate_id()
+                    line = header_text + new_tag + '\n'
+                    changed = True
+            new_lines.append(line)
+
+    if changed:
+        with open(filepath, 'w', encoding='utf-8') as f:
+            f.writelines(new_lines)
+        print(f"Updated: {filepath}")
+
+def main():
+    for filename in os.listdir('.'):
+        if filename.endswith('.qmd'):
+            process_file(filename)
+
+if __name__ == '__main__':
+    main()

### 2025-09-29 src/glossary.py

@@ -1,4 +1,3 @@
-import glob
 from typing import TypedDict
 import yaml
 
@@ -35,10 +34,10 @@ def generate_env(glossary: Glossary, acronyms: Glossary) -> str:
     gloss = {}
     acron = {}
     for item in glossary:
-        gloss[get_sec_name(item)] = f"[{item['term']}](glossary.qmd#sec-{get_sec_name(item)})"
+        gloss[get_sec_name(item)] = f"[{item['term']}](/glossary.qmd#sec-{get_sec_name(item)})"
 
     for item in acronyms:
-        acron[get_sec_name(item)] = f"[{item['term']}](glossary.qmd#sec-{get_sec_name(item)})"
+        acron[get_sec_name(item)] = f"[{item['term']}](/glossary.qmd#sec-{get_sec_name(item)})"
 
     return yaml.dump({"glossary": gloss, "acronyms": acron})
 

### 2025-09-29 src/articles/article3.qmd
sync google docs changes

@@
 
-1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
+1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the method and time specified by the Excuse Plan.
 1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
@@
 
-1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
+1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
 1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.

### 2025-09-29 src/articles/article6.qmd
sync google docs changes

@@
 
-1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c) no later than six weeks before the beginning of the Fall Semester.
+1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c)  and CAB Treasurer Advisor no later than one month before the end of the previous semester.
+   a. The Budget Committee will work with the treasurer to create a budget to be submitted to the chapter.
 1.
@@
 The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
-   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
-1. Budget Committee
-   a. The Budget Committee (@sec-art-VI2T9PVL, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
-   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
+   a. Following approval by the chapter, the budget proposal will be presented to CAB.
 1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
@@
 Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved.
+This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).
+1. Safety Margin and Emergency Fund
+   a.
+Any money leftover for the year from the Safety Margin must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved.
 This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).
@@
 1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
+   a. Brothers will pay all financial obligations through either a physical check made out to “Beta Nu Chapter Theta Chi Fraternity” or a wireless transfer/eCheck.
+   a. A brother who pays via other methods (i.e. credit card or Apple Pay) may be subject to a fine of up to 5% of the original paid amount, to be determined by the treasurer.
+      i. If a brother wishes to bypass this fee, they must submit a deferment to be approved via @sec-art-OUD16M61, Item 3.
 1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.
@@
 1.
-{{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).
+{{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have the right to request access to all accounts, budgeting and financial software, the current ledger, and Greek Bill, excluding bank accounts, subject to the discretion of the treasurer and CAB Treasurer Advisor.
+2. {{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have the right to request access to any records or statements from the bank account (or whatever online service is currently being used). 
+3. Only the President, Treasurer, and CAB Treasurer Advisor will have access to the bank accounts.
 
@@
    a. The chair who controls the budget in question.
-      i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
+      i. If the budget is not under a particular chair, or the chair is indisposed, any non-treasurer member of {{< var acronyms.ec >}} may act as a substitute.
       i. If the chair who controls the budget is also the treasurer, any other member of {{< var acronyms.ec >}} may act as a substitute.

### 2025-09-29 src/articles/article7.qmd
sync google docs changes

@@
 1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
-1.
-If a brother or their guest violates @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, @sec-art-6GSVIPRZ, Item 3, or @sec-art-6GSVIPRZ, Item 4, they will be brought up for standards by the President, with sanctions not less than:
+1. If a brother or their guest violates the above (@sec-art-6GSVIPRZ, Items 1-4), the brother will be brought up for standards, with sanctions not less than:
    a. First Offense – $50 fine
@@
    a. Third Offense – $100 fine and recommendation for suspension to the chapter
+1.
+If a guest violates the above (@sec-art-6GSVIPRZ, Items 1-4), they will be banned from the chapter house and property.
+This ban may be rescinded by a {{< var glossary.supermajority >}} (2/3) vote of the chapter.
 1. No candles will be burned inside the house or on the chapter property.
-1. @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, and @sec-art-6GSVIPRZ, Item 3 will become null and void upon the downfall of Western Civilization.
+1. @sec-art-6GSVIPRZ, Items 1-4 will become null and void upon the downfall of Western Civilization.
+   a. A necessary (but not sufficient) condition for the downfall of Western Civilization is the dissolution and nullification of these bylaws.
+      i. The above item is a Catch-22. No, you cannot do anything about it.
 
@@
    a. The following brothers are exempt from this policy:
-      i. 1st year students
       i. Commuter Students
@@
       i. Those who are on Co-op, Study Abroad, or a similar program
-      i. Those who were ineligible or exempt at the beginning of the school year\
+      i. Those who were ineligible or exempt at the beginning of the school year (e.g. first year students)
+      i. Those with a prior binding lease or housing contract that extends into the semester that they would live in the house
       i. Those with a prohibitive medical condition as approved by Case Western Reserve University ({{< var acronyms.cwru >}})
 
-1. The following brothers must live in the chapter house:
-   a. President
-   a. Vice President
-   a. Vice President of Health and Safety
-   a. Treasurer
-   a. Marshal
-   a. Recruitment Chair
-   a. Scholarship Chair
+1. All elected members of EC, excepting the President and Treasurer may live out of the house upon being elected, but beginning their first Fall semester in office, must live in the house.
+   a. This superseded the exemptions of @sec-art-71TPHUXH, Item 1a
+   a. The President and Treasurer must live in house the first full (not necessarily Fall!) semester of their office
+
+1. The following brothers must live in the chapter house. This superseded the exemptions of @sec-art-71TPHUXH, Item 1a:
+   a. All elected members of EC (subject to @sec-art-71TPHUXH, Item 2)
    a. House Manager 
+   a. Detail manager
    a. Food Steward
@@
 1.
-In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, including {{< var glossary.deferment >}}s.
+In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, excluding {{< var glossary.deferment >}}s.
    a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.
@@
    a.
-Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of the Vice President.
+Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of {{< var acronyms.ec >}}.
+      i. This option does not apply to any positions listen in @sec-art-71TPHUXH, Item 3
       i. The house may not be dropped below capacity.
@@
          1.
-Of the brothers with the highest {{< var glossary.roster-number >}} among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.
+Of the brothers who wish to move out, select the number of brothers that would bring the house to capacity via a mutually acceptable method.
+If no acceptable method if found, the brothers with the lowest {{< var glossary.roster-number >}}s will move out and the remaining brothers will live in house such that the house is at capacity.
 
    a.
-If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
-      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
+If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers with the lowest {{< var glossary.roster-number >}} will be forced to move out.
       i. Brothers listed in @sec-art-71TPHUXH, Item 2 cannot be forced to live out of the house.
+      i. In the Spring semester, no brother who lived in the house during the Fall semester can be forced to live out of the house via this item (@sec-art-C89656BJ, Item 1b).
 
@@
 
-1. Room 205 is reserved for the President unless they waive this right.
-
 1. Room assignments will be made by the Vice President following these guidelines:
-
    a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:

### 2025-09-29 src/articles/article8.qmd
add scholarship updates

@@
 
+1. The Theta Chi Scholar Award
+   a.
+May be bestowed on up to three active brothers each semester for their achievements at the university, whether that may be by coursework, research, work, teaching experience, athletics, extracurricular activities, anything else that makes him an outstanding member of the {{< var acronym.cwru >}} community, brother of Theta Chi, and citizen of the world.
+No brother may receive this award two semesters of CWRU enrollment in a row.
+   a. Will consist of a certificate of appropriate construction and suitable wording which describes the accomplishments for which the certificate is being presented.
+   a. The giving procedure, in direct exception to @sec-art-WWI418WD will be as follows:
+      i.
+Nominations will be opened for no shorter than two weeks.
+Any brother eligible to vote may, at any time when nominations are open, nominate any active member of the fraternity.
+To do so requires a second.
+      i.
+Any brother who is nominated may accept the nomination before nominations close by way of informing the Scholarship Chair of his acceptance and explaining why he thinks he is an exemplar of on-campus achievement among the members of the fraternity.
+      i.
+The Standards Board will discuss each nominee.
+In this discussion, the consideration will be of the ideals of the award, listed in Point A, with the stipulation that this award is meant to be open to brothers who are a role model in any way listed above – one does not need to be exemplary in every area to still be an example.
+No member of the Standards Board may contribute to discussion regarding their own scholarship if they themselves have been nominated, but they are welcome to discuss the award in context of other brothers.
+Although the Scholarship Chair and President may be aware of an individual brother’s {{< var acronyms.gpa >}}, they are not allowed to disclose this information unless the brother in question has provided it with their application.
+      i. The Standards Board will decide, by majority vote, at most three applicants who are deserving of the title of Theta Chi Scholar for the semester. 
+      i. These brothers will be announced at a suitable time before the end of the semester. For the spring semester, this should be at the Scholarship Dinner.
+
 1. The chapter may give out any other awards subject to the procedures defined in @sec-art-WWI418WD.

### 2025-09-29 src/articles/article3.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

@@
 
-1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
+1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the {{< var acronym.ibl >}}.
 1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.

### 2025-09-29 src/articles/article4.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

@@
 1. All brothers eligible to vote must vote.
-1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
+1. Only active brothers who are required to pay local dues and are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
 1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
-1. A brother not required to pay local dues is ineligible to vote.
 1. Unless specified in @sec-art-N8IIFY4C, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.
@@
    a. New Members for Initiation
-   b. Officer Elections
-   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
-   d. At a suspension trial
-   e. To retain a candidate who was not initiated the previous semester
+   a. Officer Elections
+   a. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
+   a. At a suspension trial
 
@@
    a. The Second Guard and the Chaplain will collect and count the {{< var glossary.ballot >}}s.
-   b. The chaplain will confirm the count and repeat the results to the presiding officer.
-   c. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
-   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.
+   a. The chaplain will confirm the count and repeat the results to the presiding officer.
+   a. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
+   a. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.
 
@@
 {{< var glossary.ballot >}}ing on New Members for Initiation will be in accordance with the International Bylaws ({{< var acronyms.ibl >}}) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
-   b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.
+   a. New Members must be approved by a ¾ vote of eligible voting members of the active chapter - including those who are not present - to be initiated.
 
@@
    a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
-   b. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
-   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.
+   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
+   a. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

### 2025-09-29 src/articles/article5.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

@@
    a. Serves as a liaison between the chapter and community health services.
-   a. Organizes events on 7 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year.
+   a. Organizes events on 5 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year in accordance with the five areas of Sacred Purpose.
    a. Maintains house medical kit.
@@
    a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.
+   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
+   a. Releases a weekly TWIOX (This Week in Theta Chi) newsletter to the alumni mailing list
 
@@
    a. Records all transactions made by the chapter.
-   a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
+   a. Will provide a written report at the request of any brother which includes all payments paid out, all monies received, current bank account balances, and budget updates.
    a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
@@
    a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph f.
-   a. Will submit a plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
+   a. Will submit a Marshal Plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
    a. Will reserve a location for initiation.
@@
    a. Serves as chair of the Philanthropy and Service Committee.
-   a. Ensures the chapter meets the Greek Life goals for service.
+   a. Ensures the chapter meets the Greek Life goals for service and philanthropy.
    a. Informs the chapter of service and philanthropy opportunities.

### 2025-09-29 build.sh
clean old script

@@ -1,3 +1,0 @@
-#!/usr/bin/env bash
-
-nix build --experimental-features "nix-command flakes" .#deploy

### 2025-09-29 src/articles/article8.qmd
fix cwru typo article 8

@@
    a.
-May be bestowed on up to three active brothers each semester for their achievements at the university, whether that may be by coursework, research, work, teaching experience, athletics, extracurricular activities, anything else that makes him an outstanding member of the {{< var acronym.cwru >}} community, brother of Theta Chi, and citizen of the world.
+May be bestowed on up to three active brothers each semester for their achievements at the university, whether that may be by coursework, research, work, teaching experience, athletics, extracurricular activities, anything else that makes him an outstanding member of the {{< var acronyms.cwru >}} community, brother of Theta Chi, and citizen of the world.
 No brother may receive this award two semesters of CWRU enrollment in a row.

### 2025-09-29 src/articles/article12.qmd
remove redundant backslashes

@@
    a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
-   a. Failure to maintain confidentiality of all proceedings of the board.\
+   a. Failure to maintain confidentiality of all proceedings of the board.
    a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
@@
 1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
-   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.\
+   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.
    a. If a plea is not received within the twenty-four hours specified above, a {{< var glossary.no-contest-plea >}} will be entered.

### 2025-09-29 src/articles/article5.qmd
remove redundant backslashes

@@
       i. The chapter will be allowed not less than five minutes to discuss.
-      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
+      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.
    a. Pledges will be allowed to vote in the election in direct exception to the above @sec-art-GW6C9D29, Item 2.
@@
    a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
-   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).\
+   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).
    a. Serves as chair of Standards Board.
@@
    a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
-   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
+   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.
    a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
@@
    a. Performs all duties specified by the Greek Life Office, {{< var acronyms.ifc >}}, and the University.
-   a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:\
+   a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:
       i. A plan for the creation of Scholarship contracts for all brothers.
@@
    a. Performs all duties stated in the I{{< var acronyms.ibl >}}BL Article V, Section 6, paragraph h.
-   a. Assists alumni relations chair with the alumni database.\
+   a. Assists alumni relations chair with the alumni database.
    a. Ensures that pictures are taken at chapter events.
@@
 
-1. Alumni Relations Chair\
+1. Alumni Relations Chair
    a. Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation and sends out the Alumni newsletter before the last day of classes.
@@
 1. Food Steward
-   a. Works with a chef or catering service to maintain a brotherhood meal plan.\
+   a. Works with a chef or catering service to maintain a brotherhood meal plan.
    a. Ensures the service chosen for the meal plan is paid for according to the agreement with the chef or catering service.
@@
       i. Vice President
-      i. Vice President of Health and Safety\
+      i. Vice President of Health and Safety
       i. Secretary
@@
          1. Work toward the goals of the committee.
-   b. Operational Committees\
+   b. Operational Committees
       i. Ad hoc committees

### 2025-09-29 src/appendices/appendix1.qmd
Fix glossary
fix appendix references

@@
-# Appendix A
+# A: {{< var acronyms.ec >}} Interpretations {.unnumbered} {#sec-art-BW7GLKA5}
 
-## EC Interpretations
-
-1. Academic warning is treated the same way as Academic Probation when a brother has not had classes for a semester.
+1. Academic warning is treated the same way as {{< var glossary.academic-probation >}} when a brother has not had classes for a semester.
 1. Standards Board does NOT need to automatically recommend a brother for suspension if said brother is brought up for standards with the possibility of suspension.

### 2025-09-29 src/articles/article13.qmd

@@
 1. Witnesses may volunteer to speak on behalf or against the charges.
-   a. The witnesses may volunteer by giving a written message to the Arbiter stating their intent to participate and stance at least three hours before the hearing.\
+   a. The witnesses may volunteer by giving a written message to the Arbiter stating their intent to participate and stance at least three hours before the hearing.
    a. Witnesses will be advised by the Arbiter that they are not to discuss the hearing or the accusation outside of the hearing.
@@
 
-1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:\
+1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:
    a. Counseling

### 2025-09-29 src/articles/article4.qmd

@@
    a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
-   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
+   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.
    a. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

### 2025-10-23 src/articles/article11.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling

@@
       i. Missing a mandatory event without an accepted excuse will count as unexcused.
-      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
+      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.
       i. A brother who has three unexcused mandatory events throughout the semester will be {{< var glossary.staggard >}}.

### 2025-10-23 src/articles/article3.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling

--- 2025-09-29 src/articles/article3.qmd
@@
 
-1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
+1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the {{< var acronyms.ibl >}}.
 1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.

### 2025-10-23 src/tag-articles.py

@@ -1,9 +1,9 @@
-import os
+from collections.abc import Iterator
 import re
 import random
 import string
+from pathlib import Path
 
-# Constants
 HEADER_PATTERN = re.compile(r'^(##? .+?)(\s*\{#.*\})?\s*$')
 TAG_TEMPLATE = ' {#sec-art-%s}'
 ID_LENGTH = 8
@@ -11,11 +11,11 @@ ID_LENGTH = 8
 def generate_id() -> str:
     return ''.join(random.choices(string.ascii_uppercase + string.digits, k=ID_LENGTH))
 
-def process_file(filepath):
+def process_file(filepath: Path):
     changed = False
-    new_lines = []
+    new_lines: list[str] = []
 
-    with open(filepath, 'r', encoding='utf-8') as f:
+    with filepath.open("r") as f:
         for line in f:
             match = HEADER_PATTERN.match(line)
             if match:
@@ -27,14 +27,14 @@ def process_file(filepath):
             new_lines.append(line)
 
     if changed:
-        with open(filepath, 'w', encoding='utf-8') as f:
+        with filepath.open("w") as f:
             f.writelines(new_lines)
         print(f"Updated: {filepath}")
 
 def main():
-    for filename in os.listdir('.'):
-        if filename.endswith('.qmd'):
-            process_file(filename)
+    pathes: Iterator[Path] = Path('.').glob("**/*.qmd")
+    for path in pathes:
+        process_file(path)
 
 if __name__ == '__main__':
     main()

### 2025-11-02 src/appendices/appendix1.qmd
fix labeling
update ec interpretation

@@
-# A: {{< var acronyms.ec >}} Interpretations {.unnumbered} {#sec-art-BW7GLKA5}
+# A: EC Interpretations {#sec-art-BW7GLKA5}
 
@@
 1. When adding interpretations, make sure to reference the particular bylaw being interpreted and the year the interpretation was made.
+1.
+A brother who has been suspended cannot be present at any event with any sort of official restriction on individuals present.
+Such events include, but are not limited to, mixers, rush events, chapter, and any ritual ceremony.
+
+   A suspended brother, should they be present at an event open to the public in the capacity of a member of the public should be expected to act as a member of the public.
+As such, they may be asked to leave at any time, for any reason, by a member of EC or the event lead.
+Such a suspended brother should not and cannot represent Theta Chi in any capacity.

### 2025-11-02 src/articles/article5.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling
update in accordance with https://docs.google.com/document/d/16Bhp1ZhyKaanmR8jaZSP-depL2DxAZ5dGMxIQ4VR0w4 (#7)

@@
    a. Ensures legislation records are up to date.
-   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
+   a. Adds all permanent legislation to the appropriate appendix (@sec-art-LGUUVLYZ) as outlined in @sec-art-Q8OV40FK.
    a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
@@
    a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.
-   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
+   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
    a. Releases a weekly TWIOX (This Week in Theta Chi) newsletter to the alumni mailing list
@@
 
-1. Philanthropy and Service Chair
-   a. Serves as chair of the Philanthropy and Service Committee.
-   a. Ensures the chapter meets the Greek Life goals for service and philanthropy.
-   a. Informs the chapter of service and philanthropy opportunities.
+1. Philanthropy Chair
+   a. Serves as chair of the Philanthropy Committee.
+   a. Ensures the chapter meets the Greek Life goals for philanthropy.
+   a. Informs the chapter of philanthropy opportunities.
+   a. Responsible for planning and holding one philanthropy event per semester.
+   a. Responsible for having one philanthropy event per academic year benefit the USO.
+   a. Serves as a member of {{< var acronyms.ccc >}}.
+
+1. Service Chair
+   a. Serves as chair of the Service Committee.
+   a. Ensures the chapter meets the Greek Life goals for service.
+   a. Informs the chapter of service opportunities.
+   a. Responsible for planning and holding at least one service event for the chapter per semester.
+   a. Responsible for tracking the service hours of active brothers.
    a. Serves as a member of {{< var acronyms.ccc >}}.
@@
    a. Standard Committees
-      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
-         1. Alumni Relations Committee and Member Development Committee
-         1. Health and Safety Committee and Scholarship Committee
-         1. Philanthropy and Service Committee and Social Committee
-         1. Public Relations Committee and Recruitment Committee
+
+      i. The list of Standard committees is as follows:
+         1. Alumni Relations Committee
+         1. Member Development Committee
+         1. Health and Safety Committee
+         1. Scholarship Committee
+         1. Philanthropy Committee
+         1. Service Committee
+         1. Social Committee
+         1. Public Relations Committee
+         1. Recruitment Committee
       i. All Standard committees will do the following:

### 2025-12-14 src/articles/article10.qmd
Scholarship updates (#12)

@@
    a. Grade release forms must be filled out prior to the due date for midterm grades.
+   a. Grades must be directly self reported to the Scholarship Chair within one week of the GLO report release if the grades are missing from the report.
+   a. If the GLO report is not released within two weeks into classes, grades must be self reported to the Scholarship Chair within one week.
+   a. Midterm grades must be reported directly to the Scholarship Chair within 2 weeks of the grades being released.
 
